### 2021-03-05 machineLearningModelsForAgriculture.tex
Add files via upload

%
% Angol nyelvű szakdolgozat minta az Eszterházy Károly Egyetem hallgatóinak.
%

\documentclass[
% without options: one-sided printing, online version
% twoside,       % two-sided printing
]{thesis-ekf}
\setcounter{secnumdepth}{5}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{natbib}
\usepackage{lipsum}
\usepackage{pgfplots}
\usetikzlibrary{intersections}
\usepackage{csquotes}
\renewcommand{\mkbegdispquote}[2]{\itshape}
\usepackage{listings}
\usepackage{color}
\usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
	language=Python,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	stringstyle=\color{mauve},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3
}
\usepackage{graphicx}
\begin{document}
\institute{Eszterhazy Karoly University}
\title{Machine Learning Model for Agricultural Data Applications}
\author{Adeyemo Adedeji Charles\\Computer Science BSc}
\supervisor{Bence Bogdandy\\Associate Professor}
\city{Eger}
\date{2020}
\maketitle

\tableofcontents

\chapter*{Introduction}

\todo{This is a Text that will appear in the margin}

Intelligence is the ability to process information to inform future decisions. The field of Artificial Intelligence is the field which focuses on building algorithm models (in this case, Artificial Intelligence \cite{black2009books} Algorithms) that can do this as well - that is - process information to inform future decisions.

Machine Learning itself is a subset of AI that focuses on teaching a machine how to do this without being explicitly programmed.

Deep Learning is a subset of Machine Learning which takes this idea even further. It allows us to automatically extract the useful pieces of information needed to inform these future predictions.

Availability of localized and external data can help to practice *Precision Agriculture*

 Like all other neural networks, deep-learning models don't take as input raw text:
 they only work with numeric tensors. Vectorizing text is the process of transforming text
 into numeric tensors. This can be done in multiple ways

\chapter{Related Works}
\section{Data Science}
Data Science encompasses making awesome visualizations and models using data. As a field of Computer Science, it has created as much positive impact in our society. Impact could be in the form of insights, in the form of data products or in the form of product recommendations for a company. In order to achieve these things, we need tools like writing code, machine learning models or data visualizations.

According to this article by Usama Fayyad \cite{fayyad1996data} data mining is referred to  as the overall process of discovering useful information from data. William S. Cleveland, \cite{cleveland2001data}   who at that time was a Distinguished Member of Technical Staff in the Statistics Research Department at Bell Labs, Murray Hill, defined data science as it is used today. He did that by combining computer science with data mining. He made statistics a lot more technical because he believed it would expand the possibilities of data mining and produce a powerful force for innovation. Now, we can take advantage of computational power for statistics.

\subsection{Technical Advancement}
Around this time, \textbf{web 2.0} emerged. Websites aren't simply digital pamphlets anymore, but a medium for shared experience among millions of users. These are websites like:
\begin{itemize}
	\item \textbf{MySpace:} 2003
	\item \textbf{Facebook:} 2004
	\item \textbf{YouTube:} 2005	
\end{itemize}

As users, we can now interact with these websites - post, comment, share - leaving our digital footprints on the Internet. That's a lot of data and soon enough, it became too much to handle using traditional technologies. This opened a world of possibilities in finding insights using data. So the rise in data sparked the rise of data science to support the needs of businesses to draw insights from their massive unstructured data sets. This abundance of data now makes it possible to train machines with a data-driven rather than a knowledge-driven approach. Deep learning is no longer an abstract academic concept in this thesis paper. It is a tangible useful class of machine learning model for agricultural data applications.

\section{Machine Learning Workflow}
From predicting economic growth to detecting cancers, Machine Learning has granted computer systems entirely new abilities. The first step to solving a Machine Learning task is to define the problem and assemble a data-set. The data-set has to be one with integrity. Choosing a measure of success and deciding on a validation protocol are the next logical steps. The most important step in building a Machine Learning model is the preparation of the data. It won't occur in a real-life situation that raw data is ready to be fed into a machine model.

Once the data is ready, the model can be built. At first, we build one that over-fits. Afterwards this model is regularized and its hyper-parameters tuned.

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{workflow.png}
	\caption{Machine Learning Workflow.}
	\label{fig:workflow}
\end{figure}

Figure \ref{fig:workflow} shows the workflow of a typical Machine Learning model.

%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////

\chapter{Methods}
\section{Data Science}
Data Science is a subset of Computer Science and Mathematics. This subset introduces a new paradigm which creates algorithms for computers and robots. It combines statistics with Computer Science. Data Science also involves the use of machine learning algorithms for prediction.

Machine Learning is a novel part of Data Science and it encompasses the ability of machines to learn from examples. These models are categorized as either \textbf{\textit{Supervised}} or \textbf{\textit{Unsupervised}} Machine Learning models.

In the field of Data Science, mathematics is very important. This is because principles within mathematics help in the detection of patterns and algorithm construction. In the application of such algorithms in data science, the comprehension of different conceptions of statistics and probability theory is crucial. Notions include Regression, Maximum Likelihood Estimation, distribution's comprehension (Binomial, Bernoulli, Gaussian (Normal)), and Bayes's Theorem.

\subsection{Supervised Learning} %Dev Later
Supervised learning is further categorized as  either \textbf{\textit{Regression}} or \textbf{\textit{Classification.}} The main difference between Regression and Classification is that the output variable in Regression is numerical while that for Classification is categorical. In other words, Regression predicts a quantity while  Classification predicts a label.

\subsubsection{Machine Learning model - Regression}
In this 1998 article, \cite{zeger1988regression} Scot Zeger posits the analysis of a regression model with a time series. Linear Regression is a basic offshoot of Regression. The predicted output of a Linear Regression model is continuous with a constant slope. The 2 main types of Linear Regression are simple and multivariate regression.

Simple linear regression can be explained with the slope-intercept form, where \textit{m} and \textit{b} are the variables the algorithm learns to produce the most accurate predictions. \textit{x} in this case represents the input data while \textit{y} the prediction.

\begin{equation}
	y = m x + b
\end{equation}

Multivariate regression is a method with more than one output variable that calculates a single regression model. If a multivariate regression model has more than one predictor variable, the system is a multivariate multiple regression.

\subsubsection{Machine Learning model - Classification}

In this 2006 paper by Kevin P. Murphy \cite{murphy2006naive} he defines a \textbf{classifier} as a function \textit{f} that maps input feature vectors to output classes. This classifier is derived from the \textbf{Bayes' Theorem}

A classification is a tool used to assign groups to a data set in order to assist in detailed forecasts and analysis. You are introduced to an existing data-set with classification algorithms and are aware of the groups of individual instances; with this information, a predictive model can then be created to solve the following problem: For any future instance in the data-set to which a particular instance belongs. Max Entropy, K-Nearest Neighbor, and Naive Bayes are among the types of classification algorithms.

\begin{equation}
	\label{eq:bayes}
	P(\theta | \textbf{D}) = P(\theta ) \frac{P(\textbf{D} |\theta)}{P(\textbf{D})},
\end{equation}

\subsection{Unsupervised Learning}
%leave AS-_is

\section{Machine Learning Workflow}
One of the fundamental goals of Data Engineering is to develop data pipelines. A Data pipeline means taking data from point A (in an operational system) and then moving it to point B (into something that can be analyzed by data scientists).
The data set used for this thesis paper was gotten from the Food and Agriculture Organization of the United Nations. This organization is tasked with creating a zero-hunger World. Starting from 1945, this organization has amassed a wealth of data-set archives from its member countries all over the world. My focus is on Hungary thus, making my contribution to creating a zero-hunger Hungary.

According to the official website,\cite{division_2000}
\begin{displayquote}
	"FAOSTAT provides free access to food and agriculture data for over 245 countries and territories and covers all FAO regional groupings from 1961 to the most recent year available."
\end{displayquote}

To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices. In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.

Different data sets are available separately. For the purpose of this thesis, I narrowed down on wheat. I adopted a consistent time-frame. 1965 to 2002. The approach to this was: Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.

\section{Neural Networks}
A neural network is a collection of algorithms that, through a mechanism that mimics the way the human brain works, aim to identify fundamental connections in a data set \cite{jain1999recurrent}.  Neural networks, in this context, apply to neuron frameworks, either biological or artificial in nature. Neural networks may respond to evolving inputs, so the network delivers the best possible outcome without the performance parameters having to be revamped. In the development of trading systems, the notion of neural networks, which has its origins in artificial intelligence, is rapidly gaining prominence.\citealp*{krose1993introduction}.

The biological neuron relations are modeled as weights. An excitation relation is reflected by a positive weight, whereas negative values mean inhibitory connections. Each input is updated and summarized by a weight. A linear combination is related to this practice. Finally, the amplitude of the output is regulated by an activation function. A reasonable performance range, for example, is usually between 0 and 1, or it may be −1 and 1.

\section{Recurring Neural Network}

A recurrent Neural Network(RNN) is a type of Neural Network in which the previous phase output is fed to the current stage as an input. Both the inputs and outputs are independent of each other in conventional neural networks, but in situations such as where it is important to predict the next word of a sentence, the prior words are needed and so the past words need to be recalled. RNN thus came into being, which, with the aid of a Hidden Layer, fixed this problem. Hidden State, which recalls any details about a sequence, is the key and most significant aspect of RNN.\cite{jain1999recurrent}

By giving all layers the same weights and preferences, RNN transforms the independent activation into dependent activation, thereby reducing the difficulty of increasing parameters and memorizing each previous output by giving each output to the next hidden layer as an input.
Therefore, all three layers should be merged into a single recurring layer such that the weights and biases of all the hidden layers are the same.

The formula for calculating the current state:

\[Ht = f(ht-1, Xt)\]

\textit{where} \textbf{H} is the current state, \textbf{ht-1} is the previous state and \textbf{Xt} is the inpunt state.

\subsection{GRU}  % DOn't Touch
\subsection{LSTM}
What is LSTM: It's the \textbf{Long short Term Memory} This networks rely on a gated cell to track information throughout many time-steps. How do LSTM work?

\begin{itemize}
	\item Forget: The lSTM forget their irrelevant history.

	\item Store: They perform computation to store relevant parts of new information.

	\item Update: They use the above items 1 and 2 to update their internal state.

	\item Output: Finally, they generate an output.
\end{itemize}

In summary, LSTMs help with uninterrupted gradient flow.

\section{Deep Learning}
\subsection{Machine Learning vs Deep Learning}

%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////////////////////////////////////////////////////////

\chapter{Implementation}
\section{Data Science - Engineering}

The process of collecting raw data from sources, transforming it so that it matches our system's requirements and loading it into a data-set is know as \textbf{ETL.} This \textit{acronym} represents \textit{Extract - Transform - Load.}

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{etl.jpg}
	\caption{Extract Transform Load.}
	\label{fig:ETL}
\end{figure}

Figure \ref{fig:ETL} shows the ETL process.

This raw data set contains lots of columns which are not necessary. The next step will be to clean the data by dropping these unnecessary columns.

\subsection{Data Extraction.}

As mentioned in the previous chapter, the source of data for the purpose of this thesis was the Food and Agriculture Organization of the United Nations. To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices. In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.

Different data sets are available separately. For the purpose of this thesis, I narrowed down on wheat. I adopted a consistent time-frame (\textbf{1965 to 2002}). The approach to this was: \textit{Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.}

To make the downloaded data set globally available, I uploaded it to my GitHub repository.\cite{adeyemo_2020}

\begin{lstlisting}[language=Python]
	url_wheatArea = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
	-Agricultural-Data-Applications/master/wheatArea.csv'

	url_wheatGrossProduction = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
	-Agricultural-Data-Applications/master/wheatGrossProductionValue.csv'

	url_wheatProductionQuantity = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
	-Agricultural-Data-Applications/master/wheatProductionQuantity.csv'

	url_wheatYield = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
	-Agricultural-Data-Applications/master/wheatYield.csv'
\end{lstlisting}

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Area_Head.png}
	\caption{Raw Data Area.}
	\label{fig:Areaa_Head1}
\end{figure}

Figure \ref{fig:Areaa_Head1} shows the top 5 rows of the Data Set.

Each set of data set contained lots of columns which are repetitive and irrelevant to the task at hand. These columns include: \textit{"Domain Code","Domain",
	"Area Code","Area","Element Code","Element","Item Code","Item",
	"Year Code","Unit","Flag","Flag Description","Note"}

\subsection{Data Cleaning} 
The repetitive columns constitute noise which isn't required. I drop these to narrow down on the vital data necessary for my task. Two columns are left: \textit{"Year", "Value".} Since the word \textit{"Value"} appears in the different data-sets, it's renamed here as \textit{"Area(Hectares)"} to clearly indicate that this value refers to the measurement of the area.

\begin{lstlisting}[language=Python]
	df_wheatArea.drop(columns=["Domain Code","Domain",
	"Area Code","Area","Element Code","Element","Item Code","Item",
	"Year Code","Unit","Flag","Flag Description","Note"], axis=1, inplace=True)

	df_wheatArea.columns = ['Year', 'Area(Hectares)']

	df_wheatArea.head()
\end{lstlisting}

A similar transformation is performed on the other data-sets. The resulting individual data-sets are: 
\begin{figure}
	\centering
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{areaHectares.png}
		\caption{Area}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{.24\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{gpv.png}
		\caption{G.P.V}
		\label{fig:sub2}
	\end{subfigure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{yield.png}
		\caption{Yield}
		\label{fig:sub3}
	\end{subfigure}
	\begin{subfigure}{.24\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{quantityTonnes.png}
		\caption{Quantity}
		\label{fig:sub4}
	\end{subfigure}

	\caption{Individual Transformed Data-Sets}
	\label{fig:heads}
\end{figure}

\section{Implementing Machine Learning Work Flow}

\subsection{Assembling the Data Set}
\section{How I implemented the Neural Networks}
\section{Recurring Neural Network}
\section{Deep Learning}

\chapter{Results}
\section{Neural Networks}
In this section, I will describe the Progression from Normal Neural network to Recurring Neural Networks - RNN. In the end, I'll show that the GRU works well and I have solved what I set out to do. 
it should be here
\subsection{Subsection title}
Neural Networks and more advanced technologies. Right now we use Pandas for everything and it's enough, except when it's not. The more advanced we go into tech, the more basic the Machine Learning tools.

Some Machine Learning models are very dependent on used materials. SCI-KIT uses the most basic of Neural networks. What you'll notice from GPV-Take 1 is that you can't create modern systems with SCI-KIT because it is the highest level of abstraction.

Here, I'll need to show the results of the Google Colab Notebook - Gross Production Value 1 and the abysmal results I got using SCI-KIT

We use SCI-KIT for scaling. It implements it very well. Train - Test - Split
\cite{ponce1989engineering}

\chapter{Discussion}
\section{Section title}
\subsection{Subsection title}

\chapter{Summary}
\section{Section title}
\subsection{Subsection title}

\bibliographystyle{plain}
\bibliography{reference}
\end{document}

### 2021-03-05 paper.tex
Rename machineLearningModelsForAgriculture.tex to paper.tex
Template

--- 2021-03-05 machineLearningModelsForAgriculture.tex
@@
 \begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{workflow.png}
+	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/workflow.png}
 	\caption{Machine Learning Workflow.}
@@
 \begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{etl.jpg}
+	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/etl.jpg}
 	\caption{Extract Transform Load.}
@@
 \begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Area_Head.png}
+	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/Area_Head.png}
 	\caption{Raw Data Area.}
@@
 		\centering
-		\includegraphics[width=.4\linewidth]{areaHectares.png}
+		\includegraphics[width=.4\linewidth]{fig/areaHectares.png}
 		\caption{Area}
@@
 		\centering
-		\includegraphics[width=.4\linewidth]{gpv.png}
+		\includegraphics[width=.4\linewidth]{fig/gpv.png}
 		\caption{G.P.V}
@@
 		\centering
-		\includegraphics[width=.4\linewidth]{yield.png}
+		\includegraphics[width=.4\linewidth]{fig/yield.png}
 		\caption{Yield}
@@
 		\centering
-		\includegraphics[width=.4\linewidth]{quantityTonnes.png}
+		\includegraphics[width=.4\linewidth]{fig/quantityTonnes.png}
 		\caption{Quantity}

### 2021-03-12 chapters/discussion.tex
Layout Changes

--- 2021-03-05 machineLearningModelsForAgriculture.tex
@@
-%
-% Angol nyelvű szakdolgozat minta az Eszterházy Károly Egyetem hallgatóinak.
-%
-
-\documentclass[
-% without options: one-sided printing, online version
-% twoside,       % two-sided printing
-]{thesis-ekf}
-\setcounter{secnumdepth}{5}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage{natbib}
-\usepackage{lipsum}
-\usepackage{pgfplots}
-\usetikzlibrary{intersections}
-\usepackage{csquotes}
-\renewcommand{\mkbegdispquote}[2]{\itshape}
-\usepackage{listings}
-\usepackage{color}
-\usepackage{subcaption}
-\usepackage[colorinlistoftodos]{todonotes}
-
-\definecolor{dkgreen}{rgb}{0,0.6,0}
-\definecolor{gray}{rgb}{0.5,0.5,0.5}
-\definecolor{mauve}{rgb}{0.58,0,0.82}
-
-\lstset{frame=tb,
-	language=Python,
-	aboveskip=3mm,
-	belowskip=3mm,
-	showstringspaces=false,
-	columns=flexible,
-	basicstyle={\small\ttfamily},
-	numbers=none,
-	numberstyle=\tiny\color{gray},
-	keywordstyle=\color{blue},
-	commentstyle=\color{dkgreen},
-	stringstyle=\color{mauve},
-	breaklines=true,
-	breakatwhitespace=true,
-	tabsize=3
-}
-\usepackage{graphicx}
-\begin{document}
-\institute{Eszterhazy Karoly University}
-\title{Machine Learning Model for Agricultural Data Applications}
-\author{Adeyemo Adedeji Charles\\Computer Science BSc}
-\supervisor{Bence Bogdandy\\Associate Professor}
-\city{Eger}
-\date{2020}
-\maketitle
-
-\tableofcontents
-
-\chapter*{Introduction}
-
-\todo{This is a Text that will appear in the margin}
-
-Intelligence is the ability to process information to inform future decisions.
-The field of Artificial Intelligence is the field which focuses on building algorithm models (in this case, Artificial Intelligence \cite{black2009books} Algorithms) that can do this as well - that is - process information to inform future decisions.
-
-Machine Learning itself is a subset of AI that focuses on teaching a machine how to do this without being explicitly programmed.
-
-Deep Learning is a subset of Machine Learning which takes this idea even further. It allows us to automatically extract the useful pieces of information needed to inform these future predictions.
-
-Availability of localized and external data can help to practice *Precision Agriculture*
-
- Like all other neural networks, deep-learning models don't take as input raw text:
- they only work with numeric tensors. Vectorizing text is the process of transforming text
- into numeric tensors. This can be done in multiple ways
-
-\chapter{Related Works}
-\section{Data Science}
-Data Science encompasses making awesome visualizations and models using data.
-As a field of Computer Science, it has created as much positive impact in our society.
-Impact could be in the form of insights, in the form of data products or in the form of product recommendations for a company.
-In order to achieve these things, we need tools like writing code, machine learning models or data visualizations.
-
-According to this article by Usama Fayyad \cite{fayyad1996data} data mining is referred to  as the overall process of discovering useful information from data.
-William S.
-Cleveland, \cite{cleveland2001data}   who at that time was a Distinguished Member of Technical Staff in the Statistics Research Department at Bell Labs, Murray Hill, defined data science as it is used today.
-He did that by combining computer science with data mining.
-He made statistics a lot more technical because he believed it would expand the possibilities of data mining and produce a powerful force for innovation.
-Now, we can take advantage of computational power for statistics.
-
-\subsection{Technical Advancement}
-Around this time, \textbf{web 2.0} emerged. Websites aren't simply digital pamphlets anymore, but a medium for shared experience among millions of users. These are websites like:
-\begin{itemize}
-	\item \textbf{MySpace:} 2003
-	\item \textbf{Facebook:} 2004
-	\item \textbf{YouTube:} 2005	
-\end{itemize}
-
-As users, we can now interact with these websites - post, comment, share - leaving our digital footprints on the Internet.
-That's a lot of data and soon enough, it became too much to handle using traditional technologies.
-This opened a world of possibilities in finding insights using data.
-So the rise in data sparked the rise of data science to support the needs of businesses to draw insights from their massive unstructured data sets.
-This abundance of data now makes it possible to train machines with a data-driven rather than a knowledge-driven approach.
-Deep learning is no longer an abstract academic concept in this thesis paper.
-It is a tangible useful class of machine learning model for agricultural data applications.
-
-\section{Machine Learning Workflow}
-From predicting economic growth to detecting cancers, Machine Learning has granted computer systems entirely new abilities.
-The first step to solving a Machine Learning task is to define the problem and assemble a data-set.
-The data-set has to be one with integrity.
-Choosing a measure of success and deciding on a validation protocol are the next logical steps.
-The most important step in building a Machine Learning model is the preparation of the data.
-It won't occur in a real-life situation that raw data is ready to be fed into a machine model.
-
-Once the data is ready, the model can be built. At first, we build one that over-fits. Afterwards this model is regularized and its hyper-parameters tuned.
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{workflow.png}
-	\caption{Machine Learning Workflow.}
-	\label{fig:workflow}
-\end{figure}
-
-Figure \ref{fig:workflow} shows the workflow of a typical Machine Learning model.
-
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-
-\chapter{Methods}
-\section{Data Science}
-Data Science is a subset of Computer Science and Mathematics.
-This subset introduces a new paradigm which creates algorithms for computers and robots.
-It combines statistics with Computer Science.
-Data Science also involves the use of machine learning algorithms for prediction.
-
-Machine Learning is a novel part of Data Science and it encompasses the ability of machines to learn from examples.
-These models are categorized as either \textbf{\textit{Supervised}} or \textbf{\textit{Unsupervised}} Machine Learning models.
-
-In the field of Data Science, mathematics is very important.
-This is because principles within mathematics help in the detection of patterns and algorithm construction.
-In the application of such algorithms in data science, the comprehension of different conceptions of statistics and probability theory is crucial.
-Notions include Regression, Maximum Likelihood Estimation, distribution's comprehension (Binomial, Bernoulli, Gaussian (Normal)), and Bayes's Theorem.
-
-\subsection{Supervised Learning} %Dev Later
-Supervised learning is further categorized as  either \textbf{\textit{Regression}} or \textbf{\textit{Classification.}} The main difference between Regression and Classification is that the output variable in Regression is numerical while that for Classification is categorical.
-In other words, Regression predicts a quantity while  Classification predicts a label.
-
-\subsubsection{Machine Learning model - Regression}
-In this 1998 article, \cite{zeger1988regression} Scot Zeger posits the analysis of a regression model with a time series.
-Linear Regression is a basic offshoot of Regression.
-The predicted output of a Linear Regression model is continuous with a constant slope.
-The 2 main types of Linear Regression are simple and multivariate regression.
-
-Simple linear regression can be explained with the slope-intercept form, where \textit{m} and \textit{b} are the variables the algorithm learns to produce the most accurate predictions.
-\textit{x} in this case represents the input data while \textit{y} the prediction.
-
-\begin{equation}
-	y = m x + b
-\end{equation}
-
-Multivariate regression is a method with more than one output variable that calculates a single regression model.
-If a multivariate regression model has more than one predictor variable, the system is a multivariate multiple regression.
-
-\subsubsection{Machine Learning model - Classification}
-
-In this 2006 paper by Kevin P.
-Murphy \cite{murphy2006naive} he defines a \textbf{classifier} as a function \textit{f} that maps input feature vectors to output classes.
-This classifier is derived from the \textbf{Bayes' Theorem}
-
-A classification is a tool used to assign groups to a data set in order to assist in detailed forecasts and analysis.
-You are introduced to an existing data-set with classification algorithms and are aware of the groups of individual instances; with this information, a predictive model can then be created to solve the following problem: For any future instance in the data-set to which a particular instance belongs.
-Max Entropy, K-Nearest Neighbor, and Naive Bayes are among the types of classification algorithms.
-
-\begin{equation}
-	\label{eq:bayes}
-	P(\theta | \textbf{D}) = P(\theta ) \frac{P(\textbf{D} |\theta)}{P(\textbf{D})},
-\end{equation}
-
-\subsection{Unsupervised Learning}
-%leave AS-_is
-
-\section{Machine Learning Workflow}
-One of the fundamental goals of Data Engineering is to develop data pipelines.
-A Data pipeline means taking data from point A (in an operational system) and then moving it to point B (into something that can be analyzed by data scientists).
-The data set used for this thesis paper was gotten from the Food and Agriculture Organization of the United Nations.
-This organization is tasked with creating a zero-hunger World.
-Starting from 1945, this organization has amassed a wealth of data-set archives from its member countries all over the world.
-My focus is on Hungary thus, making my contribution to creating a zero-hunger Hungary.
-
-According to the official website,\cite{division_2000}
-\begin{displayquote}
-	"FAOSTAT provides free access to food and agriculture data for over 245 countries and territories and covers all FAO regional groupings from 1961 to the most recent year available."
-\end{displayquote}
-
-To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices.
-In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.
-
-Different data sets are available separately.
-For the purpose of this thesis, I narrowed down on wheat.
-I adopted a consistent time-frame.
-1965 to 2002.
-The approach to this was: Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.
-
-\section{Neural Networks}
-A neural network is a collection of algorithms that, through a mechanism that mimics the way the human brain works, aim to identify fundamental connections in a data set \cite{jain1999recurrent}.
-Neural networks, in this context, apply to neuron frameworks, either biological or artificial in nature.
-Neural networks may respond to evolving inputs, so the network delivers the best possible outcome without the performance parameters having to be revamped.
-In the development of trading systems, the notion of neural networks, which has its origins in artificial intelligence, is rapidly gaining prominence.\citealp*{krose1993introduction}.
-
-The biological neuron relations are modeled as weights.
-An excitation relation is reflected by a positive weight, whereas negative values mean inhibitory connections.
-Each input is updated and summarized by a weight.
-A linear combination is related to this practice.
-Finally, the amplitude of the output is regulated by an activation function.
-A reasonable performance range, for example, is usually between 0 and 1, or it may be −1 and 1.
-
-\section{Recurring Neural Network}
-
-A recurrent Neural Network(RNN) is a type of Neural Network in which the previous phase output is fed to the current stage as an input.
-Both the inputs and outputs are independent of each other in conventional neural networks, but in situations such as where it is important to predict the next word of a sentence, the prior words are needed and so the past words need to be recalled.
-RNN thus came into being, which, with the aid of a Hidden Layer, fixed this problem.
-Hidden State, which recalls any details about a sequence, is the key and most significant aspect of RNN.\cite{jain1999recurrent}
-
-By giving all layers the same weights and preferences, RNN transforms the independent activation into dependent activation, thereby reducing the difficulty of increasing parameters and memorizing each previous output by giving each output to the next hidden layer as an input.
-Therefore, all three layers should be merged into a single recurring layer such that the weights and biases of all the hidden layers are the same.
-
-The formula for calculating the current state:
-
-\[Ht = f(ht-1, Xt)\]
-
-\textit{where} \textbf{H} is the current state, \textbf{ht-1} is the previous state and \textbf{Xt} is the inpunt state.
-
-\subsection{GRU}  % DOn't Touch
-\subsection{LSTM}
-What is LSTM: It's the \textbf{Long short Term Memory} This networks rely on a gated cell to track information throughout many time-steps. How do LSTM work?
-
-\begin{itemize}
-	\item Forget: The lSTM forget their irrelevant history.
-
-	\item Store: They perform computation to store relevant parts of new information.
-
-	\item Update: They use the above items 1 and 2 to update their internal state.
-
-	\item Output: Finally, they generate an output.
-\end{itemize}
-
-In summary, LSTMs help with uninterrupted gradient flow.
-
-\section{Deep Learning}
-\subsection{Machine Learning vs Deep Learning}
-
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-
-\chapter{Implementation}
-\section{Data Science - Engineering}
-
-The process of collecting raw data from sources, transforming it so that it matches our system's requirements and loading it into a data-set is know as \textbf{ETL.} This \textit{acronym} represents \textit{Extract - Transform - Load.}
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{etl.jpg}
-	\caption{Extract Transform Load.}
-	\label{fig:ETL}
-\end{figure}
-
-Figure \ref{fig:ETL} shows the ETL process.
-
-This raw data set contains lots of columns which are not necessary. The next step will be to clean the data by dropping these unnecessary columns.
-
-\subsection{Data Extraction.}
-
-As mentioned in the previous chapter, the source of data for the purpose of this thesis was the Food and Agriculture Organization of the United Nations.
-To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices.
-In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.
-
-Different data sets are available separately.
-For the purpose of this thesis, I narrowed down on wheat.
-I adopted a consistent time-frame (\textbf{1965 to 2002}).
-The approach to this was: \textit{Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.}
-
-To make the downloaded data set globally available, I uploaded it to my GitHub repository.\cite{adeyemo_2020}
-
-\begin{lstlisting}[language=Python]
-	url_wheatArea = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatArea.csv'
-
-	url_wheatGrossProduction = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatGrossProductionValue.csv'
-
-	url_wheatProductionQuantity = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatProductionQuantity.csv'
-
-	url_wheatYield = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatYield.csv'
-\end{lstlisting}
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Area_Head.png}
-	\caption{Raw Data Area.}
-	\label{fig:Areaa_Head1}
-\end{figure}
-
-Figure \ref{fig:Areaa_Head1} shows the top 5 rows of the Data Set.
-
-Each set of data set contained lots of columns which are repetitive and irrelevant to the task at hand. These columns include: \textit{"Domain Code","Domain",
-	"Area Code","Area","Element Code","Element","Item Code","Item",
-	"Year Code","Unit","Flag","Flag Description","Note"}
-
-\subsection{Data Cleaning} 
-The repetitive columns constitute noise which isn't required.
-I drop these to narrow down on the vital data necessary for my task.
-Two columns are left: \textit{"Year", "Value".} Since the word \textit{"Value"} appears in the different data-sets, it's renamed here as \textit{"Area(Hectares)"} to clearly indicate that this value refers to the measurement of the area.
-
-\begin{lstlisting}[language=Python]
-	df_wheatArea.drop(columns=["Domain Code","Domain",
-	"Area Code","Area","Element Code","Element","Item Code","Item",
-	"Year Code","Unit","Flag","Flag Description","Note"], axis=1, inplace=True)
-
-	df_wheatArea.columns = ['Year', 'Area(Hectares)']
-
-	df_wheatArea.head()
-\end{lstlisting}
-
-A similar transformation is performed on the other data-sets. The resulting individual data-sets are: 
-\begin{figure}
-	\centering
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{areaHectares.png}
-		\caption{Area}
-		\label{fig:sub1}
-	\end{subfigure}%
-	\begin{subfigure}{.24\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{gpv.png}
-		\caption{G.P.V}
-		\label{fig:sub2}
-	\end{subfigure}
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{yield.png}
-		\caption{Yield}
-		\label{fig:sub3}
-	\end{subfigure}
-	\begin{subfigure}{.24\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{quantityTonnes.png}
-		\caption{Quantity}
-		\label{fig:sub4}
-	\end{subfigure}
-
-	\caption{Individual Transformed Data-Sets}
-	\label{fig:heads}
-\end{figure}
-
-\section{Implementing Machine Learning Work Flow}
-
-\subsection{Assembling the Data Set}
-\section{How I implemented the Neural Networks}
-\section{Recurring Neural Network}
-\section{Deep Learning}
-
-\chapter{Results}
-\section{Neural Networks}
-In this section, I will describe the Progression from Normal Neural network to Recurring Neural Networks - RNN. In the end, I'll show that the GRU works well and I have solved what I set out to do. 
-it should be here
-\subsection{Subsection title}
-Neural Networks and more advanced technologies.
-Right now we use Pandas for everything and it's enough, except when it's not.
-The more advanced we go into tech, the more basic the Machine Learning tools.
-
-Some Machine Learning models are very dependent on used materials.
-SCI-KIT uses the most basic of Neural networks.
-What you'll notice from GPV-Take 1 is that you can't create modern systems with SCI-KIT because it is the highest level of abstraction.
-
-Here, I'll need to show the results of the Google Colab Notebook - Gross Production Value 1 and the abysmal results I got using SCI-KIT
-
-We use SCI-KIT for scaling. It implements it very well. Train - Test - Split
-\cite{ponce1989engineering}
-
-\chapter{Discussion}
 \section{Section title}
 \subsection{Subsection title}
-
-\chapter{Summary}
-\section{Section title}
-\subsection{Subsection title}
-
-\bibliographystyle{plain}
-\bibliography{reference}
-\end{document}

### 2021-03-12 chapters/implementation.tex
Layout Changes

--- 2021-03-05 paper.tex
@@
-%
-% Angol nyelvű szakdolgozat minta az Eszterházy Károly Egyetem hallgatóinak.
-%
-
-\documentclass[
-% without options: one-sided printing, online version
-% twoside,       % two-sided printing
-]{thesis-ekf}
-\setcounter{secnumdepth}{5}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage{natbib}
-\usepackage{lipsum}
-\usepackage{pgfplots}
-\usetikzlibrary{intersections}
-\usepackage{csquotes}
-\renewcommand{\mkbegdispquote}[2]{\itshape}
-\usepackage{listings}
-\usepackage{color}
-\usepackage{subcaption}
-\usepackage[colorinlistoftodos]{todonotes}
-
-\definecolor{dkgreen}{rgb}{0,0.6,0}
-\definecolor{gray}{rgb}{0.5,0.5,0.5}
-\definecolor{mauve}{rgb}{0.58,0,0.82}
-
-\lstset{frame=tb,
-	language=Python,
-	aboveskip=3mm,
-	belowskip=3mm,
-	showstringspaces=false,
-	columns=flexible,
-	basicstyle={\small\ttfamily},
-	numbers=none,
-	numberstyle=\tiny\color{gray},
-	keywordstyle=\color{blue},
-	commentstyle=\color{dkgreen},
-	stringstyle=\color{mauve},
-	breaklines=true,
-	breakatwhitespace=true,
-	tabsize=3
-}
-\usepackage{graphicx}
-\begin{document}
-\institute{Eszterhazy Karoly University}
-\title{Machine Learning Model for Agricultural Data Applications}
-\author{Adeyemo Adedeji Charles\\Computer Science BSc}
-\supervisor{Bence Bogdandy\\Associate Professor}
-\city{Eger}
-\date{2020}
-\maketitle
-
-\tableofcontents
-
-\chapter*{Introduction}
-
-\todo{This is a Text that will appear in the margin}
-
-Intelligence is the ability to process information to inform future decisions.
-The field of Artificial Intelligence is the field which focuses on building algorithm models (in this case, Artificial Intelligence \cite{black2009books} Algorithms) that can do this as well - that is - process information to inform future decisions.
-
-Machine Learning itself is a subset of AI that focuses on teaching a machine how to do this without being explicitly programmed.
-
-Deep Learning is a subset of Machine Learning which takes this idea even further. It allows us to automatically extract the useful pieces of information needed to inform these future predictions.
-
-Availability of localized and external data can help to practice *Precision Agriculture*
-
- Like all other neural networks, deep-learning models don't take as input raw text:
- they only work with numeric tensors. Vectorizing text is the process of transforming text
- into numeric tensors. This can be done in multiple ways
-
-\chapter{Related Works}
-\section{Data Science}
-Data Science encompasses making awesome visualizations and models using data.
-As a field of Computer Science, it has created as much positive impact in our society.
-Impact could be in the form of insights, in the form of data products or in the form of product recommendations for a company.
-In order to achieve these things, we need tools like writing code, machine learning models or data visualizations.
-
-According to this article by Usama Fayyad \cite{fayyad1996data} data mining is referred to  as the overall process of discovering useful information from data.
-William S.
-Cleveland, \cite{cleveland2001data}   who at that time was a Distinguished Member of Technical Staff in the Statistics Research Department at Bell Labs, Murray Hill, defined data science as it is used today.
-He did that by combining computer science with data mining.
-He made statistics a lot more technical because he believed it would expand the possibilities of data mining and produce a powerful force for innovation.
-Now, we can take advantage of computational power for statistics.
-
-\subsection{Technical Advancement}
-Around this time, \textbf{web 2.0} emerged. Websites aren't simply digital pamphlets anymore, but a medium for shared experience among millions of users. These are websites like:
-\begin{itemize}
-	\item \textbf{MySpace:} 2003
-	\item \textbf{Facebook:} 2004
-	\item \textbf{YouTube:} 2005	
-\end{itemize}
-
-As users, we can now interact with these websites - post, comment, share - leaving our digital footprints on the Internet.
-That's a lot of data and soon enough, it became too much to handle using traditional technologies.
-This opened a world of possibilities in finding insights using data.
-So the rise in data sparked the rise of data science to support the needs of businesses to draw insights from their massive unstructured data sets.
-This abundance of data now makes it possible to train machines with a data-driven rather than a knowledge-driven approach.
-Deep learning is no longer an abstract academic concept in this thesis paper.
-It is a tangible useful class of machine learning model for agricultural data applications.
-
-\section{Machine Learning Workflow}
-From predicting economic growth to detecting cancers, Machine Learning has granted computer systems entirely new abilities.
-The first step to solving a Machine Learning task is to define the problem and assemble a data-set.
-The data-set has to be one with integrity.
-Choosing a measure of success and deciding on a validation protocol are the next logical steps.
-The most important step in building a Machine Learning model is the preparation of the data.
-It won't occur in a real-life situation that raw data is ready to be fed into a machine model.
-
-Once the data is ready, the model can be built. At first, we build one that over-fits. Afterwards this model is regularized and its hyper-parameters tuned.
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/workflow.png}
-	\caption{Machine Learning Workflow.}
-	\label{fig:workflow}
-\end{figure}
-
-Figure \ref{fig:workflow} shows the workflow of a typical Machine Learning model.
-
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-
-\chapter{Methods}
-\section{Data Science}
-Data Science is a subset of Computer Science and Mathematics.
-This subset introduces a new paradigm which creates algorithms for computers and robots.
-It combines statistics with Computer Science.
-Data Science also involves the use of machine learning algorithms for prediction.
-
-Machine Learning is a novel part of Data Science and it encompasses the ability of machines to learn from examples.
-These models are categorized as either \textbf{\textit{Supervised}} or \textbf{\textit{Unsupervised}} Machine Learning models.
-
-In the field of Data Science, mathematics is very important.
-This is because principles within mathematics help in the detection of patterns and algorithm construction.
-In the application of such algorithms in data science, the comprehension of different conceptions of statistics and probability theory is crucial.
-Notions include Regression, Maximum Likelihood Estimation, distribution's comprehension (Binomial, Bernoulli, Gaussian (Normal)), and Bayes's Theorem.
-
-\subsection{Supervised Learning} %Dev Later
-Supervised learning is further categorized as  either \textbf{\textit{Regression}} or \textbf{\textit{Classification.}} The main difference between Regression and Classification is that the output variable in Regression is numerical while that for Classification is categorical.
-In other words, Regression predicts a quantity while  Classification predicts a label.
-
-\subsubsection{Machine Learning model - Regression}
-In this 1998 article, \cite{zeger1988regression} Scot Zeger posits the analysis of a regression model with a time series.
-Linear Regression is a basic offshoot of Regression.
-The predicted output of a Linear Regression model is continuous with a constant slope.
-The 2 main types of Linear Regression are simple and multivariate regression.
-
-Simple linear regression can be explained with the slope-intercept form, where \textit{m} and \textit{b} are the variables the algorithm learns to produce the most accurate predictions.
-\textit{x} in this case represents the input data while \textit{y} the prediction.
-
-\begin{equation}
-	y = m x + b
-\end{equation}
-
-Multivariate regression is a method with more than one output variable that calculates a single regression model.
-If a multivariate regression model has more than one predictor variable, the system is a multivariate multiple regression.
-
-\subsubsection{Machine Learning model - Classification}
-
-In this 2006 paper by Kevin P.
-Murphy \cite{murphy2006naive} he defines a \textbf{classifier} as a function \textit{f} that maps input feature vectors to output classes.
-This classifier is derived from the \textbf{Bayes' Theorem}
-
-A classification is a tool used to assign groups to a data set in order to assist in detailed forecasts and analysis.
-You are introduced to an existing data-set with classification algorithms and are aware of the groups of individual instances; with this information, a predictive model can then be created to solve the following problem: For any future instance in the data-set to which a particular instance belongs.
-Max Entropy, K-Nearest Neighbor, and Naive Bayes are among the types of classification algorithms.
-
-\begin{equation}
-	\label{eq:bayes}
-	P(\theta | \textbf{D}) = P(\theta ) \frac{P(\textbf{D} |\theta)}{P(\textbf{D})},
-\end{equation}
-
-\subsection{Unsupervised Learning}
-%leave AS-_is
-
-\section{Machine Learning Workflow}
-One of the fundamental goals of Data Engineering is to develop data pipelines.
-A Data pipeline means taking data from point A (in an operational system) and then moving it to point B (into something that can be analyzed by data scientists).
-The data set used for this thesis paper was gotten from the Food and Agriculture Organization of the United Nations.
-This organization is tasked with creating a zero-hunger World.
-Starting from 1945, this organization has amassed a wealth of data-set archives from its member countries all over the world.
-My focus is on Hungary thus, making my contribution to creating a zero-hunger Hungary.
-
-According to the official website,\cite{division_2000}
-\begin{displayquote}
-	"FAOSTAT provides free access to food and agriculture data for over 245 countries and territories and covers all FAO regional groupings from 1961 to the most recent year available."
-\end{displayquote}
-
-To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices.
-In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.
-
-Different data sets are available separately.
-For the purpose of this thesis, I narrowed down on wheat.
-I adopted a consistent time-frame.
-1965 to 2002.
-The approach to this was: Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.
-
-\section{Neural Networks}
-A neural network is a collection of algorithms that, through a mechanism that mimics the way the human brain works, aim to identify fundamental connections in a data set \cite{jain1999recurrent}.
-Neural networks, in this context, apply to neuron frameworks, either biological or artificial in nature.
-Neural networks may respond to evolving inputs, so the network delivers the best possible outcome without the performance parameters having to be revamped.
-In the development of trading systems, the notion of neural networks, which has its origins in artificial intelligence, is rapidly gaining prominence.\citealp*{krose1993introduction}.
-
-The biological neuron relations are modeled as weights.
-An excitation relation is reflected by a positive weight, whereas negative values mean inhibitory connections.
-Each input is updated and summarized by a weight.
-A linear combination is related to this practice.
-Finally, the amplitude of the output is regulated by an activation function.
-A reasonable performance range, for example, is usually between 0 and 1, or it may be −1 and 1.
-
-\section{Recurring Neural Network}
-
-A recurrent Neural Network(RNN) is a type of Neural Network in which the previous phase output is fed to the current stage as an input.
-Both the inputs and outputs are independent of each other in conventional neural networks, but in situations such as where it is important to predict the next word of a sentence, the prior words are needed and so the past words need to be recalled.
-RNN thus came into being, which, with the aid of a Hidden Layer, fixed this problem.
-Hidden State, which recalls any details about a sequence, is the key and most significant aspect of RNN.\cite{jain1999recurrent}
-
-By giving all layers the same weights and preferences, RNN transforms the independent activation into dependent activation, thereby reducing the difficulty of increasing parameters and memorizing each previous output by giving each output to the next hidden layer as an input.
-Therefore, all three layers should be merged into a single recurring layer such that the weights and biases of all the hidden layers are the same.
-
-The formula for calculating the current state:
-
-\[Ht = f(ht-1, Xt)\]
-
-\textit{where} \textbf{H} is the current state, \textbf{ht-1} is the previous state and \textbf{Xt} is the inpunt state.
-
-\subsection{GRU}  % DOn't Touch
-\subsection{LSTM}
-What is LSTM: It's the \textbf{Long short Term Memory} This networks rely on a gated cell to track information throughout many time-steps. How do LSTM work?
-
-\begin{itemize}
-	\item Forget: The lSTM forget their irrelevant history.
-
-	\item Store: They perform computation to store relevant parts of new information.
-
-	\item Update: They use the above items 1 and 2 to update their internal state.
-
-	\item Output: Finally, they generate an output.
-\end{itemize}
-
-In summary, LSTMs help with uninterrupted gradient flow.
-
-\section{Deep Learning}
-\subsection{Machine Learning vs Deep Learning}
-
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-
-\chapter{Implementation}
 \section{Data Science - Engineering}
@@
 \cite{ponce1989engineering}
-
-\chapter{Discussion}
-\section{Section title}
-\subsection{Subsection title}
-
-\chapter{Summary}
-\section{Section title}
-\subsection{Subsection title}
-
-\bibliographystyle{plain}
-\bibliography{reference}
-\end{document}

### 2021-03-12 chapters/methods.tex
Layout Changes

--- 2021-03-05 machineLearningModelsForAgriculture.tex
@@
-%
-% Angol nyelvű szakdolgozat minta az Eszterházy Károly Egyetem hallgatóinak.
-%
-
-\documentclass[
-% without options: one-sided printing, online version
-% twoside,       % two-sided printing
-]{thesis-ekf}
-\setcounter{secnumdepth}{5}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage{natbib}
-\usepackage{lipsum}
-\usepackage{pgfplots}
-\usetikzlibrary{intersections}
-\usepackage{csquotes}
-\renewcommand{\mkbegdispquote}[2]{\itshape}
-\usepackage{listings}
-\usepackage{color}
-\usepackage{subcaption}
-\usepackage[colorinlistoftodos]{todonotes}
-
-\definecolor{dkgreen}{rgb}{0,0.6,0}
-\definecolor{gray}{rgb}{0.5,0.5,0.5}
-\definecolor{mauve}{rgb}{0.58,0,0.82}
-
-\lstset{frame=tb,
-	language=Python,
-	aboveskip=3mm,
-	belowskip=3mm,
-	showstringspaces=false,
-	columns=flexible,
-	basicstyle={\small\ttfamily},
-	numbers=none,
-	numberstyle=\tiny\color{gray},
-	keywordstyle=\color{blue},
-	commentstyle=\color{dkgreen},
-	stringstyle=\color{mauve},
-	breaklines=true,
-	breakatwhitespace=true,
-	tabsize=3
-}
-\usepackage{graphicx}
-\begin{document}
-\institute{Eszterhazy Karoly University}
-\title{Machine Learning Model for Agricultural Data Applications}
-\author{Adeyemo Adedeji Charles\\Computer Science BSc}
-\supervisor{Bence Bogdandy\\Associate Professor}
-\city{Eger}
-\date{2020}
-\maketitle
-
-\tableofcontents
-
-\chapter*{Introduction}
-
-\todo{This is a Text that will appear in the margin}
-
-Intelligence is the ability to process information to inform future decisions.
-The field of Artificial Intelligence is the field which focuses on building algorithm models (in this case, Artificial Intelligence \cite{black2009books} Algorithms) that can do this as well - that is - process information to inform future decisions.
-
-Machine Learning itself is a subset of AI that focuses on teaching a machine how to do this without being explicitly programmed.
-
-Deep Learning is a subset of Machine Learning which takes this idea even further. It allows us to automatically extract the useful pieces of information needed to inform these future predictions.
-
-Availability of localized and external data can help to practice *Precision Agriculture*
-
- Like all other neural networks, deep-learning models don't take as input raw text:
- they only work with numeric tensors. Vectorizing text is the process of transforming text
- into numeric tensors. This can be done in multiple ways
-
-\chapter{Related Works}
-\section{Data Science}
-Data Science encompasses making awesome visualizations and models using data.
-As a field of Computer Science, it has created as much positive impact in our society.
-Impact could be in the form of insights, in the form of data products or in the form of product recommendations for a company.
-In order to achieve these things, we need tools like writing code, machine learning models or data visualizations.
-
-According to this article by Usama Fayyad \cite{fayyad1996data} data mining is referred to  as the overall process of discovering useful information from data.
-William S.
-Cleveland, \cite{cleveland2001data}   who at that time was a Distinguished Member of Technical Staff in the Statistics Research Department at Bell Labs, Murray Hill, defined data science as it is used today.
-He did that by combining computer science with data mining.
-He made statistics a lot more technical because he believed it would expand the possibilities of data mining and produce a powerful force for innovation.
-Now, we can take advantage of computational power for statistics.
-
-\subsection{Technical Advancement}
-Around this time, \textbf{web 2.0} emerged. Websites aren't simply digital pamphlets anymore, but a medium for shared experience among millions of users. These are websites like:
-\begin{itemize}
-	\item \textbf{MySpace:} 2003
-	\item \textbf{Facebook:} 2004
-	\item \textbf{YouTube:} 2005	
-\end{itemize}
-
-As users, we can now interact with these websites - post, comment, share - leaving our digital footprints on the Internet.
-That's a lot of data and soon enough, it became too much to handle using traditional technologies.
-This opened a world of possibilities in finding insights using data.
-So the rise in data sparked the rise of data science to support the needs of businesses to draw insights from their massive unstructured data sets.
-This abundance of data now makes it possible to train machines with a data-driven rather than a knowledge-driven approach.
-Deep learning is no longer an abstract academic concept in this thesis paper.
-It is a tangible useful class of machine learning model for agricultural data applications.
-
-\section{Machine Learning Workflow}
-From predicting economic growth to detecting cancers, Machine Learning has granted computer systems entirely new abilities.
-The first step to solving a Machine Learning task is to define the problem and assemble a data-set.
-The data-set has to be one with integrity.
-Choosing a measure of success and deciding on a validation protocol are the next logical steps.
-The most important step in building a Machine Learning model is the preparation of the data.
-It won't occur in a real-life situation that raw data is ready to be fed into a machine model.
-
-Once the data is ready, the model can be built. At first, we build one that over-fits. Afterwards this model is regularized and its hyper-parameters tuned.
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{workflow.png}
-	\caption{Machine Learning Workflow.}
-	\label{fig:workflow}
-\end{figure}
-
-Figure \ref{fig:workflow} shows the workflow of a typical Machine Learning model.
-
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-
-\chapter{Methods}
 \section{Data Science}
@@
 \subsection{Machine Learning vs Deep Learning}
-
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-
-\chapter{Implementation}
-\section{Data Science - Engineering}
-
-The process of collecting raw data from sources, transforming it so that it matches our system's requirements and loading it into a data-set is know as \textbf{ETL.} This \textit{acronym} represents \textit{Extract - Transform - Load.}
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{etl.jpg}
-	\caption{Extract Transform Load.}
-	\label{fig:ETL}
-\end{figure}
-
-Figure \ref{fig:ETL} shows the ETL process.
-
-This raw data set contains lots of columns which are not necessary. The next step will be to clean the data by dropping these unnecessary columns.
-
-\subsection{Data Extraction.}
-
-As mentioned in the previous chapter, the source of data for the purpose of this thesis was the Food and Agriculture Organization of the United Nations.
-To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices.
-In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.
-
-Different data sets are available separately.
-For the purpose of this thesis, I narrowed down on wheat.
-I adopted a consistent time-frame (\textbf{1965 to 2002}).
-The approach to this was: \textit{Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.}
-
-To make the downloaded data set globally available, I uploaded it to my GitHub repository.\cite{adeyemo_2020}
-
-\begin{lstlisting}[language=Python]
-	url_wheatArea = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatArea.csv'
-
-	url_wheatGrossProduction = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatGrossProductionValue.csv'
-
-	url_wheatProductionQuantity = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatProductionQuantity.csv'
-
-	url_wheatYield = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatYield.csv'
-\end{lstlisting}
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Area_Head.png}
-	\caption{Raw Data Area.}
-	\label{fig:Areaa_Head1}
-\end{figure}
-
-Figure \ref{fig:Areaa_Head1} shows the top 5 rows of the Data Set.
-
-Each set of data set contained lots of columns which are repetitive and irrelevant to the task at hand. These columns include: \textit{"Domain Code","Domain",
-	"Area Code","Area","Element Code","Element","Item Code","Item",
-	"Year Code","Unit","Flag","Flag Description","Note"}
-
-\subsection{Data Cleaning} 
-The repetitive columns constitute noise which isn't required.
-I drop these to narrow down on the vital data necessary for my task.
-Two columns are left: \textit{"Year", "Value".} Since the word \textit{"Value"} appears in the different data-sets, it's renamed here as \textit{"Area(Hectares)"} to clearly indicate that this value refers to the measurement of the area.
-
-\begin{lstlisting}[language=Python]
-	df_wheatArea.drop(columns=["Domain Code","Domain",
-	"Area Code","Area","Element Code","Element","Item Code","Item",
-	"Year Code","Unit","Flag","Flag Description","Note"], axis=1, inplace=True)
-
-	df_wheatArea.columns = ['Year', 'Area(Hectares)']
-
-	df_wheatArea.head()
-\end{lstlisting}
-
-A similar transformation is performed on the other data-sets. The resulting individual data-sets are: 
-\begin{figure}
-	\centering
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{areaHectares.png}
-		\caption{Area}
-		\label{fig:sub1}
-	\end{subfigure}%
-	\begin{subfigure}{.24\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{gpv.png}
-		\caption{G.P.V}
-		\label{fig:sub2}
-	\end{subfigure}
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{yield.png}
-		\caption{Yield}
-		\label{fig:sub3}
-	\end{subfigure}
-	\begin{subfigure}{.24\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{quantityTonnes.png}
-		\caption{Quantity}
-		\label{fig:sub4}
-	\end{subfigure}
-
-	\caption{Individual Transformed Data-Sets}
-	\label{fig:heads}
-\end{figure}
-
-\section{Implementing Machine Learning Work Flow}
-
-\subsection{Assembling the Data Set}
-\section{How I implemented the Neural Networks}
-\section{Recurring Neural Network}
-\section{Deep Learning}
-
-\chapter{Results}
-\section{Neural Networks}
-In this section, I will describe the Progression from Normal Neural network to Recurring Neural Networks - RNN. In the end, I'll show that the GRU works well and I have solved what I set out to do. 
-it should be here
-\subsection{Subsection title}
-Neural Networks and more advanced technologies.
-Right now we use Pandas for everything and it's enough, except when it's not.
-The more advanced we go into tech, the more basic the Machine Learning tools.
-
-Some Machine Learning models are very dependent on used materials.
-SCI-KIT uses the most basic of Neural networks.
-What you'll notice from GPV-Take 1 is that you can't create modern systems with SCI-KIT because it is the highest level of abstraction.
-
-Here, I'll need to show the results of the Google Colab Notebook - Gross Production Value 1 and the abysmal results I got using SCI-KIT
-
-We use SCI-KIT for scaling. It implements it very well. Train - Test - Split
-\cite{ponce1989engineering}
-
-\chapter{Discussion}
-\section{Section title}
-\subsection{Subsection title}
-
-\chapter{Summary}
-\section{Section title}
-\subsection{Subsection title}
-
-\bibliographystyle{plain}
-\bibliography{reference}
-\end{document}

### 2021-03-12 chapters/relatedWorks.tex
Layout Changes

--- 2021-03-05 machineLearningModelsForAgriculture.tex
@@
-%
-% Angol nyelvű szakdolgozat minta az Eszterházy Károly Egyetem hallgatóinak.
-%
+\section{Data Science}
+\todo{Create a Diagram and have my Question in the middle. From reading my first Journal paper, I'll add key branches to the diagram.}
 
-\documentclass[
-% without options: one-sided printing, online version
-% twoside,       % two-sided printing
-]{thesis-ekf}
-\setcounter{secnumdepth}{5}
-\usepackage[T1]{fontenc}
-\usepackage[english]{babel}
-\usepackage{natbib}
-\usepackage{lipsum}
-\usepackage{pgfplots}
-\usetikzlibrary{intersections}
-\usepackage{csquotes}
-\renewcommand{\mkbegdispquote}[2]{\itshape}
-\usepackage{listings}
-\usepackage{color}
-\usepackage{subcaption}
-\usepackage[colorinlistoftodos]{todonotes}
+\todo{In the diagram - Reader can identify - This is my Diagram - This is my Question and I have the relevant things properly cited and referenced. How to add citation to a diagram. }
 
-\definecolor{dkgreen}{rgb}{0,0.6,0}
-\definecolor{gray}{rgb}{0.5,0.5,0.5}
-\definecolor{mauve}{rgb}{0.58,0,0.82}
-
-\lstset{frame=tb,
-	language=Python,
-	aboveskip=3mm,
-	belowskip=3mm,
-	showstringspaces=false,
-	columns=flexible,
-	basicstyle={\small\ttfamily},
-	numbers=none,
-	numberstyle=\tiny\color{gray},
-	keywordstyle=\color{blue},
-	commentstyle=\color{dkgreen},
-	stringstyle=\color{mauve},
-	breaklines=true,
-	breakatwhitespace=true,
-	tabsize=3
-}
-\usepackage{graphicx}
-\begin{document}
-\institute{Eszterhazy Karoly University}
-\title{Machine Learning Model for Agricultural Data Applications}
-\author{Adeyemo Adedeji Charles\\Computer Science BSc}
-\supervisor{Bence Bogdandy\\Associate Professor}
-\city{Eger}
-\date{2020}
-\maketitle
-
-\tableofcontents
-
-\chapter*{Introduction}
-
-\todo{This is a Text that will appear in the margin}
-
-Intelligence is the ability to process information to inform future decisions.
-The field of Artificial Intelligence is the field which focuses on building algorithm models (in this case, Artificial Intelligence \cite{black2009books} Algorithms) that can do this as well - that is - process information to inform future decisions.
-
-Machine Learning itself is a subset of AI that focuses on teaching a machine how to do this without being explicitly programmed.
-
-Deep Learning is a subset of Machine Learning which takes this idea even further. It allows us to automatically extract the useful pieces of information needed to inform these future predictions.
-
-Availability of localized and external data can help to practice *Precision Agriculture*
-
- Like all other neural networks, deep-learning models don't take as input raw text:
- they only work with numeric tensors. Vectorizing text is the process of transforming text
- into numeric tensors. This can be done in multiple ways
-
-\chapter{Related Works}
-\section{Data Science}
+\todo{So I'll talk about these themes from the Figure and how they are connected to my work. logically.Hence the Chapters bence said. This should be in the diagram.  }
 Data Science encompasses making awesome visualizations and models using data.
@@
 Figure \ref{fig:workflow} shows the workflow of a typical Machine Learning model.
-
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-
-\chapter{Methods}
-\section{Data Science}
-Data Science is a subset of Computer Science and Mathematics.
-This subset introduces a new paradigm which creates algorithms for computers and robots.
-It combines statistics with Computer Science.
-Data Science also involves the use of machine learning algorithms for prediction.
-
-Machine Learning is a novel part of Data Science and it encompasses the ability of machines to learn from examples.
-These models are categorized as either \textbf{\textit{Supervised}} or \textbf{\textit{Unsupervised}} Machine Learning models.
-
-In the field of Data Science, mathematics is very important.
-This is because principles within mathematics help in the detection of patterns and algorithm construction.
-In the application of such algorithms in data science, the comprehension of different conceptions of statistics and probability theory is crucial.
-Notions include Regression, Maximum Likelihood Estimation, distribution's comprehension (Binomial, Bernoulli, Gaussian (Normal)), and Bayes's Theorem.
-
-\subsection{Supervised Learning} %Dev Later
-Supervised learning is further categorized as  either \textbf{\textit{Regression}} or \textbf{\textit{Classification.}} The main difference between Regression and Classification is that the output variable in Regression is numerical while that for Classification is categorical.
-In other words, Regression predicts a quantity while  Classification predicts a label.
-
-\subsubsection{Machine Learning model - Regression}
-In this 1998 article, \cite{zeger1988regression} Scot Zeger posits the analysis of a regression model with a time series.
-Linear Regression is a basic offshoot of Regression.
-The predicted output of a Linear Regression model is continuous with a constant slope.
-The 2 main types of Linear Regression are simple and multivariate regression.
-
-Simple linear regression can be explained with the slope-intercept form, where \textit{m} and \textit{b} are the variables the algorithm learns to produce the most accurate predictions.
-\textit{x} in this case represents the input data while \textit{y} the prediction.
-
-\begin{equation}
-	y = m x + b
-\end{equation}
-
-Multivariate regression is a method with more than one output variable that calculates a single regression model.
-If a multivariate regression model has more than one predictor variable, the system is a multivariate multiple regression.
-
-\subsubsection{Machine Learning model - Classification}
-
-In this 2006 paper by Kevin P.
-Murphy \cite{murphy2006naive} he defines a \textbf{classifier} as a function \textit{f} that maps input feature vectors to output classes.
-This classifier is derived from the \textbf{Bayes' Theorem}
-
-A classification is a tool used to assign groups to a data set in order to assist in detailed forecasts and analysis.
-You are introduced to an existing data-set with classification algorithms and are aware of the groups of individual instances; with this information, a predictive model can then be created to solve the following problem: For any future instance in the data-set to which a particular instance belongs.
-Max Entropy, K-Nearest Neighbor, and Naive Bayes are among the types of classification algorithms.
-
-\begin{equation}
-	\label{eq:bayes}
-	P(\theta | \textbf{D}) = P(\theta ) \frac{P(\textbf{D} |\theta)}{P(\textbf{D})},
-\end{equation}
-
-\subsection{Unsupervised Learning}
-%leave AS-_is
-
-\section{Machine Learning Workflow}
-One of the fundamental goals of Data Engineering is to develop data pipelines.
-A Data pipeline means taking data from point A (in an operational system) and then moving it to point B (into something that can be analyzed by data scientists).
-The data set used for this thesis paper was gotten from the Food and Agriculture Organization of the United Nations.
-This organization is tasked with creating a zero-hunger World.
-Starting from 1945, this organization has amassed a wealth of data-set archives from its member countries all over the world.
-My focus is on Hungary thus, making my contribution to creating a zero-hunger Hungary.
-
-According to the official website,\cite{division_2000}
-\begin{displayquote}
-	"FAOSTAT provides free access to food and agriculture data for over 245 countries and territories and covers all FAO regional groupings from 1961 to the most recent year available."
-\end{displayquote}
-
-To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices.
-In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.
-
-Different data sets are available separately.
-For the purpose of this thesis, I narrowed down on wheat.
-I adopted a consistent time-frame.
-1965 to 2002.
-The approach to this was: Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.
-
-\section{Neural Networks}
-A neural network is a collection of algorithms that, through a mechanism that mimics the way the human brain works, aim to identify fundamental connections in a data set \cite{jain1999recurrent}.
-Neural networks, in this context, apply to neuron frameworks, either biological or artificial in nature.
-Neural networks may respond to evolving inputs, so the network delivers the best possible outcome without the performance parameters having to be revamped.
-In the development of trading systems, the notion of neural networks, which has its origins in artificial intelligence, is rapidly gaining prominence.\citealp*{krose1993introduction}.
-
-The biological neuron relations are modeled as weights.
-An excitation relation is reflected by a positive weight, whereas negative values mean inhibitory connections.
-Each input is updated and summarized by a weight.
-A linear combination is related to this practice.
-Finally, the amplitude of the output is regulated by an activation function.
-A reasonable performance range, for example, is usually between 0 and 1, or it may be −1 and 1.
-
-\section{Recurring Neural Network}
-
-A recurrent Neural Network(RNN) is a type of Neural Network in which the previous phase output is fed to the current stage as an input.
-Both the inputs and outputs are independent of each other in conventional neural networks, but in situations such as where it is important to predict the next word of a sentence, the prior words are needed and so the past words need to be recalled.
-RNN thus came into being, which, with the aid of a Hidden Layer, fixed this problem.
-Hidden State, which recalls any details about a sequence, is the key and most significant aspect of RNN.\cite{jain1999recurrent}
-
-By giving all layers the same weights and preferences, RNN transforms the independent activation into dependent activation, thereby reducing the difficulty of increasing parameters and memorizing each previous output by giving each output to the next hidden layer as an input.
-Therefore, all three layers should be merged into a single recurring layer such that the weights and biases of all the hidden layers are the same.
-
-The formula for calculating the current state:
-
-\[Ht = f(ht-1, Xt)\]
-
-\textit{where} \textbf{H} is the current state, \textbf{ht-1} is the previous state and \textbf{Xt} is the inpunt state.
-
-\subsection{GRU}  % DOn't Touch
-\subsection{LSTM}
-What is LSTM: It's the \textbf{Long short Term Memory} This networks rely on a gated cell to track information throughout many time-steps. How do LSTM work?
-
-\begin{itemize}
-	\item Forget: The lSTM forget their irrelevant history.
-
-	\item Store: They perform computation to store relevant parts of new information.
-
-	\item Update: They use the above items 1 and 2 to update their internal state.
-
-	\item Output: Finally, they generate an output.
-\end{itemize}
-
-In summary, LSTMs help with uninterrupted gradient flow.
-
-\section{Deep Learning}
-\subsection{Machine Learning vs Deep Learning}
-
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-
-\chapter{Implementation}
-\section{Data Science - Engineering}
-
-The process of collecting raw data from sources, transforming it so that it matches our system's requirements and loading it into a data-set is know as \textbf{ETL.} This \textit{acronym} represents \textit{Extract - Transform - Load.}
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{etl.jpg}
-	\caption{Extract Transform Load.}
-	\label{fig:ETL}
-\end{figure}
-
-Figure \ref{fig:ETL} shows the ETL process.
-
-This raw data set contains lots of columns which are not necessary. The next step will be to clean the data by dropping these unnecessary columns.
-
-\subsection{Data Extraction.}
-
-As mentioned in the previous chapter, the source of data for the purpose of this thesis was the Food and Agriculture Organization of the United Nations.
-To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices.
-In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.
-
-Different data sets are available separately.
-For the purpose of this thesis, I narrowed down on wheat.
-I adopted a consistent time-frame (\textbf{1965 to 2002}).
-The approach to this was: \textit{Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.}
-
-To make the downloaded data set globally available, I uploaded it to my GitHub repository.\cite{adeyemo_2020}
-
-\begin{lstlisting}[language=Python]
-	url_wheatArea = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatArea.csv'
-
-	url_wheatGrossProduction = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatGrossProductionValue.csv'
-
-	url_wheatProductionQuantity = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatProductionQuantity.csv'
-
-	url_wheatYield = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatYield.csv'
-\end{lstlisting}
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Area_Head.png}
-	\caption{Raw Data Area.}
-	\label{fig:Areaa_Head1}
-\end{figure}
-
-Figure \ref{fig:Areaa_Head1} shows the top 5 rows of the Data Set.
-
-Each set of data set contained lots of columns which are repetitive and irrelevant to the task at hand. These columns include: \textit{"Domain Code","Domain",
-	"Area Code","Area","Element Code","Element","Item Code","Item",
-	"Year Code","Unit","Flag","Flag Description","Note"}
-
-\subsection{Data Cleaning} 
-The repetitive columns constitute noise which isn't required.
-I drop these to narrow down on the vital data necessary for my task.
-Two columns are left: \textit{"Year", "Value".} Since the word \textit{"Value"} appears in the different data-sets, it's renamed here as \textit{"Area(Hectares)"} to clearly indicate that this value refers to the measurement of the area.
-
-\begin{lstlisting}[language=Python]
-	df_wheatArea.drop(columns=["Domain Code","Domain",
-	"Area Code","Area","Element Code","Element","Item Code","Item",
-	"Year Code","Unit","Flag","Flag Description","Note"], axis=1, inplace=True)
-
-	df_wheatArea.columns = ['Year', 'Area(Hectares)']
-
-	df_wheatArea.head()
-\end{lstlisting}
-
-A similar transformation is performed on the other data-sets. The resulting individual data-sets are: 
-\begin{figure}
-	\centering
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{areaHectares.png}
-		\caption{Area}
-		\label{fig:sub1}
-	\end{subfigure}%
-	\begin{subfigure}{.24\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{gpv.png}
-		\caption{G.P.V}
-		\label{fig:sub2}
-	\end{subfigure}
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{yield.png}
-		\caption{Yield}
-		\label{fig:sub3}
-	\end{subfigure}
-	\begin{subfigure}{.24\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{quantityTonnes.png}
-		\caption{Quantity}
-		\label{fig:sub4}
-	\end{subfigure}
-
-	\caption{Individual Transformed Data-Sets}
-	\label{fig:heads}
-\end{figure}
-
-\section{Implementing Machine Learning Work Flow}
-
-\subsection{Assembling the Data Set}
-\section{How I implemented the Neural Networks}
-\section{Recurring Neural Network}
-\section{Deep Learning}
-
-\chapter{Results}
-\section{Neural Networks}
-In this section, I will describe the Progression from Normal Neural network to Recurring Neural Networks - RNN. In the end, I'll show that the GRU works well and I have solved what I set out to do. 
-it should be here
-\subsection{Subsection title}
-Neural Networks and more advanced technologies.
-Right now we use Pandas for everything and it's enough, except when it's not.
-The more advanced we go into tech, the more basic the Machine Learning tools.
-
-Some Machine Learning models are very dependent on used materials.
-SCI-KIT uses the most basic of Neural networks.
-What you'll notice from GPV-Take 1 is that you can't create modern systems with SCI-KIT because it is the highest level of abstraction.
-
-Here, I'll need to show the results of the Google Colab Notebook - Gross Production Value 1 and the abysmal results I got using SCI-KIT
-
-We use SCI-KIT for scaling. It implements it very well. Train - Test - Split
-\cite{ponce1989engineering}
-
-\chapter{Discussion}
-\section{Section title}
-\subsection{Subsection title}
-
-\chapter{Summary}
-\section{Section title}
-\subsection{Subsection title}
-
-\bibliographystyle{plain}
-\bibliography{reference}
-\end{document}

### 2021-03-12 paper.tex
Layout Changes

--- 2021-03-05 machineLearningModelsForAgriculture.tex
@@
 \usepackage{graphicx}
+\graphicspath{{fig/}}
+
 \begin{document}
+
 \institute{Eszterhazy Karoly University}
@@
 \author{Adeyemo Adedeji Charles\\Computer Science BSc}
-\supervisor{Bence Bogdandy\\Associate Professor}
+
+\supervisor{Bence Bogdandy\\Associate Professor
+		\\bogdandy.bence@uni-eszterhazy.hu}
 \city{Eger}
-\date{2020}
+\date{2020/21}
 \maketitle
+
+\begin{abstract}
+	Prediction of economical growth is a complex task which is essential for planning sustainable economy.
+	Economy has a wide range of indicators that are monitored and recorded by governments and international organizations, such as, the Food and Agriculture Organization.
+	Agricultural data set of the Food and Agriculture Organization has records on production of crops and other agricultural products whose production strongly relates to the Gross Domestic Product of many countries.
+	Assuming that total crop production and agricultural economy growth are highly related, the production of crops and total value of income from agriculture can be learnt by sequential machine learning models.
+	Recurrent Neural Networks excel in learning time series and sequential data. 
+	This thesis presents experimental results on training various recurrent neural networks for modeling the changes of Agricultural and Gross Domestic Products.  
+	Our experimental results showed that the models could achieve \textbf{85}\% accuracy. 	
+\end{abstract}
+
+\chapter*{Dedication}
+
+To my mentor and supervisor, Bogdandy Bence without whom this dream would have remained a dream.
 
@@
 
-\todo{This is a Text that will appear in the margin}
+\todo{This is has to be concise. What is the purpose of my Thesis? What is the aim and the Objectives
+for researching this particular area}
 
@@
 \chapter{Related Works}
-\section{Data Science}
-Data Science encompasses making awesome visualizations and models using data.
-As a field of Computer Science, it has created as much positive impact in our society.
-Impact could be in the form of insights, in the form of data products or in the form of product recommendations for a company.
-In order to achieve these things, we need tools like writing code, machine learning models or data visualizations.
+\todo{Also known as Literature. Concise. Here, I have to create a diagram that shows my thought process.}
 
-According to this article by Usama Fayyad \cite{fayyad1996data} data mining is referred to  as the overall process of discovering useful information from data.
-William S.
-Cleveland, \cite{cleveland2001data}   who at that time was a Distinguished Member of Technical Staff in the Statistics Research Department at Bell Labs, Murray Hill, defined data science as it is used today.
-He did that by combining computer science with data mining.
-He made statistics a lot more technical because he believed it would expand the possibilities of data mining and produce a powerful force for innovation.
-Now, we can take advantage of computational power for statistics.
-
-\subsection{Technical Advancement}
-Around this time, \textbf{web 2.0} emerged. Websites aren't simply digital pamphlets anymore, but a medium for shared experience among millions of users. These are websites like:
-\begin{itemize}
-	\item \textbf{MySpace:} 2003
-	\item \textbf{Facebook:} 2004
-	\item \textbf{YouTube:} 2005	
-\end{itemize}
-
-As users, we can now interact with these websites - post, comment, share - leaving our digital footprints on the Internet.
-That's a lot of data and soon enough, it became too much to handle using traditional technologies.
-This opened a world of possibilities in finding insights using data.
-So the rise in data sparked the rise of data science to support the needs of businesses to draw insights from their massive unstructured data sets.
-This abundance of data now makes it possible to train machines with a data-driven rather than a knowledge-driven approach.
-Deep learning is no longer an abstract academic concept in this thesis paper.
-It is a tangible useful class of machine learning model for agricultural data applications.
-
-\section{Machine Learning Workflow}
-From predicting economic growth to detecting cancers, Machine Learning has granted computer systems entirely new abilities.
-The first step to solving a Machine Learning task is to define the problem and assemble a data-set.
-The data-set has to be one with integrity.
-Choosing a measure of success and deciding on a validation protocol are the next logical steps.
-The most important step in building a Machine Learning model is the preparation of the data.
-It won't occur in a real-life situation that raw data is ready to be fed into a machine model.
-
-Once the data is ready, the model can be built. At first, we build one that over-fits. Afterwards this model is regularized and its hyper-parameters tuned.
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{workflow.png}
-	\caption{Machine Learning Workflow.}
-	\label{fig:workflow}
-\end{figure}
-
-Figure \ref{fig:workflow} shows the workflow of a typical Machine Learning model.
-
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
+\input{chapters/relatedWorks}
 
 \chapter{Methods}
-\section{Data Science}
-Data Science is a subset of Computer Science and Mathematics.
-This subset introduces a new paradigm which creates algorithms for computers and robots.
-It combines statistics with Computer Science.
-Data Science also involves the use of machine learning algorithms for prediction.
-
-Machine Learning is a novel part of Data Science and it encompasses the ability of machines to learn from examples.
-These models are categorized as either \textbf{\textit{Supervised}} or \textbf{\textit{Unsupervised}} Machine Learning models.
-
-In the field of Data Science, mathematics is very important.
-This is because principles within mathematics help in the detection of patterns and algorithm construction.
-In the application of such algorithms in data science, the comprehension of different conceptions of statistics and probability theory is crucial.
-Notions include Regression, Maximum Likelihood Estimation, distribution's comprehension (Binomial, Bernoulli, Gaussian (Normal)), and Bayes's Theorem.
-
-\subsection{Supervised Learning} %Dev Later
-Supervised learning is further categorized as  either \textbf{\textit{Regression}} or \textbf{\textit{Classification.}} The main difference between Regression and Classification is that the output variable in Regression is numerical while that for Classification is categorical.
-In other words, Regression predicts a quantity while  Classification predicts a label.
-
-\subsubsection{Machine Learning model - Regression}
-In this 1998 article, \cite{zeger1988regression} Scot Zeger posits the analysis of a regression model with a time series.
-Linear Regression is a basic offshoot of Regression.
-The predicted output of a Linear Regression model is continuous with a constant slope.
-The 2 main types of Linear Regression are simple and multivariate regression.
-
-Simple linear regression can be explained with the slope-intercept form, where \textit{m} and \textit{b} are the variables the algorithm learns to produce the most accurate predictions.
-\textit{x} in this case represents the input data while \textit{y} the prediction.
-
-\begin{equation}
-	y = m x + b
-\end{equation}
-
-Multivariate regression is a method with more than one output variable that calculates a single regression model.
-If a multivariate regression model has more than one predictor variable, the system is a multivariate multiple regression.
-
-\subsubsection{Machine Learning model - Classification}
-
-In this 2006 paper by Kevin P.
-Murphy \cite{murphy2006naive} he defines a \textbf{classifier} as a function \textit{f} that maps input feature vectors to output classes.
-This classifier is derived from the \textbf{Bayes' Theorem}
-
-A classification is a tool used to assign groups to a data set in order to assist in detailed forecasts and analysis.
-You are introduced to an existing data-set with classification algorithms and are aware of the groups of individual instances; with this information, a predictive model can then be created to solve the following problem: For any future instance in the data-set to which a particular instance belongs.
-Max Entropy, K-Nearest Neighbor, and Naive Bayes are among the types of classification algorithms.
-
-\begin{equation}
-	\label{eq:bayes}
-	P(\theta | \textbf{D}) = P(\theta ) \frac{P(\textbf{D} |\theta)}{P(\textbf{D})},
-\end{equation}
-
-\subsection{Unsupervised Learning}
-%leave AS-_is
-
-\section{Machine Learning Workflow}
-One of the fundamental goals of Data Engineering is to develop data pipelines.
-A Data pipeline means taking data from point A (in an operational system) and then moving it to point B (into something that can be analyzed by data scientists).
-The data set used for this thesis paper was gotten from the Food and Agriculture Organization of the United Nations.
-This organization is tasked with creating a zero-hunger World.
-Starting from 1945, this organization has amassed a wealth of data-set archives from its member countries all over the world.
-My focus is on Hungary thus, making my contribution to creating a zero-hunger Hungary.
-
-According to the official website,\cite{division_2000}
-\begin{displayquote}
-	"FAOSTAT provides free access to food and agriculture data for over 245 countries and territories and covers all FAO regional groupings from 1961 to the most recent year available."
-\end{displayquote}
-
-To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices.
-In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.
-
-Different data sets are available separately.
-For the purpose of this thesis, I narrowed down on wheat.
-I adopted a consistent time-frame.
-1965 to 2002.
-The approach to this was: Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.
-
-\section{Neural Networks}
-A neural network is a collection of algorithms that, through a mechanism that mimics the way the human brain works, aim to identify fundamental connections in a data set \cite{jain1999recurrent}.
-Neural networks, in this context, apply to neuron frameworks, either biological or artificial in nature.
-Neural networks may respond to evolving inputs, so the network delivers the best possible outcome without the performance parameters having to be revamped.
-In the development of trading systems, the notion of neural networks, which has its origins in artificial intelligence, is rapidly gaining prominence.\citealp*{krose1993introduction}.
-
-The biological neuron relations are modeled as weights.
-An excitation relation is reflected by a positive weight, whereas negative values mean inhibitory connections.
-Each input is updated and summarized by a weight.
-A linear combination is related to this practice.
-Finally, the amplitude of the output is regulated by an activation function.
-A reasonable performance range, for example, is usually between 0 and 1, or it may be −1 and 1.
-
-\section{Recurring Neural Network}
-
-A recurrent Neural Network(RNN) is a type of Neural Network in which the previous phase output is fed to the current stage as an input.
-Both the inputs and outputs are independent of each other in conventional neural networks, but in situations such as where it is important to predict the next word of a sentence, the prior words are needed and so the past words need to be recalled.
-RNN thus came into being, which, with the aid of a Hidden Layer, fixed this problem.
-Hidden State, which recalls any details about a sequence, is the key and most significant aspect of RNN.\cite{jain1999recurrent}
-
-By giving all layers the same weights and preferences, RNN transforms the independent activation into dependent activation, thereby reducing the difficulty of increasing parameters and memorizing each previous output by giving each output to the next hidden layer as an input.
-Therefore, all three layers should be merged into a single recurring layer such that the weights and biases of all the hidden layers are the same.
-
-The formula for calculating the current state:
-
-\[Ht = f(ht-1, Xt)\]
-
-\textit{where} \textbf{H} is the current state, \textbf{ht-1} is the previous state and \textbf{Xt} is the inpunt state.
-
-\subsection{GRU}  % DOn't Touch
-\subsection{LSTM}
-What is LSTM: It's the \textbf{Long short Term Memory} This networks rely on a gated cell to track information throughout many time-steps. How do LSTM work?
-
-\begin{itemize}
-	\item Forget: The lSTM forget their irrelevant history.
-
-	\item Store: They perform computation to store relevant parts of new information.
-
-	\item Update: They use the above items 1 and 2 to update their internal state.
-
-	\item Output: Finally, they generate an output.
-\end{itemize}
-
-In summary, LSTMs help with uninterrupted gradient flow.
-
-\section{Deep Learning}
-\subsection{Machine Learning vs Deep Learning}
-
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
-%////////////////////////////////////////////////////////////////////////////////////////////
+\input{chapters/methods}
 
 \chapter{Implementation}
-\section{Data Science - Engineering}
-
-The process of collecting raw data from sources, transforming it so that it matches our system's requirements and loading it into a data-set is know as \textbf{ETL.} This \textit{acronym} represents \textit{Extract - Transform - Load.}
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{etl.jpg}
-	\caption{Extract Transform Load.}
-	\label{fig:ETL}
-\end{figure}
-
-Figure \ref{fig:ETL} shows the ETL process.
-
-This raw data set contains lots of columns which are not necessary. The next step will be to clean the data by dropping these unnecessary columns.
-
-\subsection{Data Extraction.}
-
-As mentioned in the previous chapter, the source of data for the purpose of this thesis was the Food and Agriculture Organization of the United Nations.
-To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices.
-In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.
-
-Different data sets are available separately.
-For the purpose of this thesis, I narrowed down on wheat.
-I adopted a consistent time-frame (\textbf{1965 to 2002}).
-The approach to this was: \textit{Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.}
-
-To make the downloaded data set globally available, I uploaded it to my GitHub repository.\cite{adeyemo_2020}
-
-\begin{lstlisting}[language=Python]
-	url_wheatArea = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatArea.csv'
-
-	url_wheatGrossProduction = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatGrossProductionValue.csv'
-
-	url_wheatProductionQuantity = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatProductionQuantity.csv'
-
-	url_wheatYield = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for
-	-Agricultural-Data-Applications/master/wheatYield.csv'
-\end{lstlisting}
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Area_Head.png}
-	\caption{Raw Data Area.}
-	\label{fig:Areaa_Head1}
-\end{figure}
-
-Figure \ref{fig:Areaa_Head1} shows the top 5 rows of the Data Set.
-
-Each set of data set contained lots of columns which are repetitive and irrelevant to the task at hand. These columns include: \textit{"Domain Code","Domain",
-	"Area Code","Area","Element Code","Element","Item Code","Item",
-	"Year Code","Unit","Flag","Flag Description","Note"}
-
-\subsection{Data Cleaning} 
-The repetitive columns constitute noise which isn't required.
-I drop these to narrow down on the vital data necessary for my task.
-Two columns are left: \textit{"Year", "Value".} Since the word \textit{"Value"} appears in the different data-sets, it's renamed here as \textit{"Area(Hectares)"} to clearly indicate that this value refers to the measurement of the area.
-
-\begin{lstlisting}[language=Python]
-	df_wheatArea.drop(columns=["Domain Code","Domain",
-	"Area Code","Area","Element Code","Element","Item Code","Item",
-	"Year Code","Unit","Flag","Flag Description","Note"], axis=1, inplace=True)
-
-	df_wheatArea.columns = ['Year', 'Area(Hectares)']
-
-	df_wheatArea.head()
-\end{lstlisting}
-
-A similar transformation is performed on the other data-sets. The resulting individual data-sets are: 
-\begin{figure}
-	\centering
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{areaHectares.png}
-		\caption{Area}
-		\label{fig:sub1}
-	\end{subfigure}%
-	\begin{subfigure}{.24\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{gpv.png}
-		\caption{G.P.V}
-		\label{fig:sub2}
-	\end{subfigure}
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{yield.png}
-		\caption{Yield}
-		\label{fig:sub3}
-	\end{subfigure}
-	\begin{subfigure}{.24\textwidth}
-		\centering
-		\includegraphics[width=.4\linewidth]{quantityTonnes.png}
-		\caption{Quantity}
-		\label{fig:sub4}
-	\end{subfigure}
-
-	\caption{Individual Transformed Data-Sets}
-	\label{fig:heads}
-\end{figure}
-
-\section{Implementing Machine Learning Work Flow}
-
-\subsection{Assembling the Data Set}
-\section{How I implemented the Neural Networks}
-\section{Recurring Neural Network}
-\section{Deep Learning}
-
-\chapter{Results}
-\section{Neural Networks}
-In this section, I will describe the Progression from Normal Neural network to Recurring Neural Networks - RNN. In the end, I'll show that the GRU works well and I have solved what I set out to do. 
-it should be here
-\subsection{Subsection title}
-Neural Networks and more advanced technologies.
-Right now we use Pandas for everything and it's enough, except when it's not.
-The more advanced we go into tech, the more basic the Machine Learning tools.
-
-Some Machine Learning models are very dependent on used materials.
-SCI-KIT uses the most basic of Neural networks.
-What you'll notice from GPV-Take 1 is that you can't create modern systems with SCI-KIT because it is the highest level of abstraction.
-
-Here, I'll need to show the results of the Google Colab Notebook - Gross Production Value 1 and the abysmal results I got using SCI-KIT
-
-We use SCI-KIT for scaling. It implements it very well. Train - Test - Split
-\cite{ponce1989engineering}
+\input{chapters/implementation}
 
 \chapter{Discussion}
-\section{Section title}
-\subsection{Subsection title}
+\input{chapters/discussion}
 
 \chapter{Summary}
-\section{Section title}
-\subsection{Subsection title}
+\input{chapters/summary}
 

### 2021-03-13 chapters/implementation.tex
Added Python Code File

@@
 \section{Data Science - Engineering}
+\todo{Demonstrate the ability for analysis.}
+\todo{Link to Related works - Not repeating. Might look at the sections and link them}
 
+\todo{Section 1 is very interesting and further supports, or cast doubts or raises question marks about what is being said in the Related works.}
 The process of collecting raw data from sources, transforming it so that it matches our system's requirements and loading it into a data-set is know as \textbf{ETL.} This \textit{acronym} represents \textit{Extract - Transform - Load.}

### 2021-03-13 chapters/methods.tex
Layouts
Added Python Code File

@@
 \section{Data Science}
+
+\todo{It's critical that this section JUSTIFIES THE TOOLS I'm using. Think of a plumber.}
+
+\todo{I'll have to JUSTIFY my approach}
+
+\todo{I'll have to justify why I am selecting certain tools to answer my Research questions. That is the questions in the Diagram in Related Works}
+
+\todo{In addition, extract questions that go into a table. Justify why you have selected the sections and reference the Literature review. Maybe not relevant to my work.}
 Data Science is a subset of Computer Science and Mathematics.
@@
 
+Testing my commit
+
 \section{Deep Learning}

### 2021-03-13 Thesis_Model.py

@@ -1,0 +1,134 @@
+import tensorflow as tf
+import gradio as gr
+import datetime
+import pandas as pd
+import numpy as np
+import keras
+import math
+from keras.layers import LSTM
+from keras.preprocessing import sequence
+import sklearn
+from sklearn.model_selection import train_test_split
+from sklearn.preprocessing import MinMaxScaler
+from sklearn.metrics import mean_squared_error
+import matplotlib.pyplot as plt
+from keras.models import Sequential
+from keras.layers import Dense
+from keras.callbacks import TensorBoard
+
+url_wheatArea = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for-Agricultural-Data-Applications/master/wheatArea.csv'
+url_wheatGrossProduction = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for-Agricultural-Data-Applications/master/wheatGrossProductionValue.csv'
+url_wheatProductionQuantity = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for-Agricultural-Data-Applications/master/wheatProductionQuantity.csv'
+url_wheatYield = 'https://raw.githubusercontent.com/k-plasma/Machine-Learning-Models-for-Agricultural-Data-Applications/master/wheatYield.csv'
+
+
+df_wheatArea = pd.read_csv(url_wheatArea)
+df_wheatGrossProduction = pd.read_csv(url_wheatGrossProduction)
+df_wheatProductionQuantity = pd.read_csv(url_wheatProductionQuantity)
+df_wheatYield = pd.read_csv(url_wheatYield)
+
+
+df_wheatArea.drop(columns=["Domain Code","Domain",
+                         "Area Code","Area","Element Code","Element","Item Code","Item",
+                         "Year Code","Unit","Flag","Flag Description","Note"], axis=1, inplace=True)
+
+df_wheatGrossProduction.drop(columns=["Domain Code","Domain",
+                         "Area Code","Area","Element Code","Element","Item Code","Item","Year",
+                         "Year Code","Unit","Flag","Flag Description","Note"], axis=1, inplace=True)
+
+
+df_wheatProductionQuantity.drop(columns=["Domain Code","Domain",
[…]

### 2021-03-13 Thesis_Model.py
Added Python Code File2

@@ -130,5 +130,11 @@ gr.Interface(predict,
         gr.inputs.Textbox(label="Yield")
     ],
     gr.outputs.Textbox(label="GPV")).launch()
-  
+
+
+
+
+
+
+
 

### 2021-03-14 chapters/relatedWorks.tex
Rewriting the Intro - Concise - Problem Highlighted - Purpose of Research clear

@@
 \todo{So I'll talk about these themes from the Figure and how they are connected to my work. logically.Hence the Chapters bence said. This should be in the diagram.  }
+
+Intelligence is the ability to process information to inform future decisions.
+The field of Artificial Intelligence is the field which focuses on building algorithm models (in this case, Artificial Intelligence \cite{black2009books} Algorithms) that can do this as well - that is - process information to inform future decisions.
+
+Machine Learning itself is a subset of AI that focuses on teaching a machine how to do this without being explicitly programmed.
+
+Deep Learning is a subset of Machine Learning which takes this idea even further. It allows us to automatically extract the useful pieces of information needed to inform these future predictions.
+
+Availability of localized and external data can help to practice *Precision Agriculture*
+
+Like all other neural networks, deep-learning models don't take as input raw text:
+they only work with numeric tensors. Vectorizing text is the process of transforming text
+into numeric tensors. This can be done in multiple ways
+
 Data Science encompasses making awesome visualizations and models using data.

### 2021-03-14 paper.tex
Rewriting the Intro - Concise - Problem Highlighted - Purpose of Research clear

@@
 	Prediction of economical growth is a complex task which is essential for planning sustainable economy.	
-	Economy has a wide range of indicators that are monitored and recorded by governments and international organizations, such as, the Food and Agriculture Organization.
+	Economy has a wide range of indicators that are monitored and recorded by governments and international organizations, such as, the United Nations Food and Agriculture Organization.	
 	Agricultural data set of the Food and Agriculture Organization has records on production of crops and other agricultural products whose production strongly relates to the Gross Domestic Product of many countries.
+
 	Assuming that total crop production and agricultural economy growth are highly related, the production of crops and total value of income from agriculture can be learnt by sequential machine learning models.
 	Recurrent Neural Networks excel in learning time series and sequential data. 
-	This thesis presents experimental results on training various recurrent neural networks for modeling the changes of Agricultural and Gross Domestic Products.  
-	Our experimental results showed that the models could achieve \textbf{85}\% accuracy. 	
+	This study presents experimental results on training various recurrent neural networks for predicting the Gross Production Value of a particular agricultural product - wheat - given certain data point parameters.
+
+	This predictive model also plays a role in the Hungarian economic policy as in the future it will serve a basis for the calculation of the expected income for a specific crop.
 \end{abstract}
@@
 
-Intelligence is the ability to process information to inform future decisions.
-The field of Artificial Intelligence is the field which focuses on building algorithm models (in this case, Artificial Intelligence \cite{black2009books} Algorithms) that can do this as well - that is - process information to inform future decisions.
+Gross Domestic Product (GDP) is one of the most popular economical term and parameter for the indication of the well-being of a country.
+It is used by governments and international organization for critical decision making based on the size and performance of an economy.
+So, it is very important to compute and measure it accurately.
+Having a precise measurement of GDP according to the defined way is essentially impossible because it's a quantitative value which doesn't take all social indicators into account.We are thus able to give an estimated, acceptable value of the GDP.
 
-Machine Learning itself is a subset of AI that focuses on teaching a machine how to do this without being explicitly programmed.
+This work is based on how the GDP is affected.
+There are a number of factors which affects the GDP positively or negatively.
+These factors could be domestic or global.
+The internal factors include political conditions, the state of peace, government public policies, business policies etc.
+Global factor could be international relations with other nations, relations with the neighboring nations, distances from international markets and access to global markets.
 
-Deep Learning is a subset of Machine Learning which takes this idea even further. It allows us to automatically extract the useful pieces of information needed to inform these future predictions.
+Exploring the history of economic and financial studies, it can be found that over 600 parameters can be identified \cite{richardson2020nowcasting} as predictors of GDP.
+After the innovation of this notion, its effectors have been analyzed in three distinct ways: qualitative analysis, statistical analysis and relational analysis.
+Qualitative analysis has often been the most popular in journalistic circles.
+While statistical analysis has been quite prevalent in economists circles.
+The use of machine learning is quite recent.
+It has made possible the exploration of several unanswered latent problems in economies.\cite{richardson2020nowcasting, milavcic2017application, kumar2019novel}
 
-Availability of localized and external data can help to practice *Precision Agriculture*
+This research is focused on the use of deep learning methods to study the impact of agriculture on the economy of Hungary. It focuses on:
 
- Like all other neural networks, deep-learning models don't take as input raw text:
- they only work with numeric tensors. Vectorizing text is the process of transforming text
- into numeric tensors. This can be done in multiple ways
+\begin{itemize}
+	\item Period: \textbf{1961 - 2016}
+	\item Crop: \textbf{Wheat}
+	\item Data points: \textbf{Area, Quantity, Yield}
+\end{itemize}
+
+\textbf{Bence - input}Or it can be rewritten as: This research studies the effect of wheat production in Hungary between 1961 - 2016 and its direct effect on the Gross Domestic Product.
+
+The rest of the document describes the role of neural networks in agricultural research.
+The methods of this proposed research are described in chapter II.
+After the comprehensive implementation in chapter III of the methods employed, the results of the works are discussed in chapters IV and V respectively.
 

### 2021-03-17 chapters/relatedWorks.tex
Intro-Abstract(100%)-Related Works(50%)
Related Works completed

@@
+\todo{So I'll talk about these themes from the Figure and how they are connected to my work. logically.Hence the Chapters bence said. This should be in the diagram.  }
+
 \section{Data Science}
-\todo{Create a Diagram and have my Question in the middle. From reading my first Journal paper, I'll add key branches to the diagram.}
 
-\todo{In the diagram - Reader can identify - This is my Diagram - This is my Question and I have the relevant things properly cited and referenced. How to add citation to a diagram. }
-
-\todo{So I'll talk about these themes from the Figure and how they are connected to my work. logically.Hence the Chapters bence said. This should be in the diagram.  }
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.75\textwidth, height=0.75\columnwidth]{Related_Works.png}
+	\caption{Related Works.\protect\cite{tkacz2001neural, chuku2017intelligent, kiss2011significance, yamak2019comparison}}
+	\label{fig:relatedWorks}
+\end{figure}
 
@@
 Machine Learning itself is a subset of AI that focuses on teaching a machine how to do this without being explicitly programmed.
-
-Deep Learning is a subset of Machine Learning which takes this idea even further. It allows us to automatically extract the useful pieces of information needed to inform these future predictions.
-
-Availability of localized and external data can help to practice *Precision Agriculture*
-
-Like all other neural networks, deep-learning models don't take as input raw text:
-they only work with numeric tensors. Vectorizing text is the process of transforming text
-into numeric tensors. This can be done in multiple ways
+Deep Learning is a subset of Machine Learning which takes this idea even further.
+It allows us to automatically extract the useful pieces of information needed to inform these future predictions.
 
@@
 
-According to this article by Usama Fayyad \cite{fayyad1996data} data mining is referred to  as the overall process of discovering useful information from data.
+Tkacz's \cite{tkacz2001neural} research analyzes the Canadian GDP growth rates. His results show that artificial neural networks are superior to linear models in yearly forecasting.
+Chuku  and his colleagues \cite{chuku2017intelligent} examined GDP data from Kenya, Nigeria and South Africa.
+Their results also showed that artificial neural networks were superior to structural econometric models.
+They stated that these countries are \enquote{exposed to potential chaotic influences from commodity prices, external factors, and economic factors} \cite[p.25]{chuku2017intelligent}.
+Usama Fayyad \cite{fayyad1996data} referred to data mining as the overall process of discovering useful information from data.
 William S.
-Cleveland, \cite{cleveland2001data}   who at that time was a Distinguished Member of Technical Staff in the Statistics Research Department at Bell Labs, Murray Hill, defined data science as it is used today.
+Cleveland, \cite{cleveland2001data} who at that time was a Distinguished Member of the Technical Staff in the Statistics Research Department at Bell Labs, Murray Hill, defined data science as it is used today.
 He did that by combining computer science with data mining.
@@
 	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{workflow.png}
-	\caption{Machine Learning Workflow.}
+	\caption{Machine Learning Workflow.\protect\cite{division_2000, charfeddine2020reviewing, krose1993introduction}}
 	\label{fig:workflow}

### 2021-03-25 chapters/methods.tex
Method Dev

@@
 \todo{In addition, extract questions that go into a table. Justify why you have selected the sections and reference the Literature review. Maybe not relevant to my work.}
+
 Data Science is a subset of Computer Science and Mathematics.
 This subset introduces a new paradigm which creates algorithms for computers and robots.
-It combines statistics with Computer Science.
 Data Science also involves the use of machine learning algorithms for prediction.
-
-Machine Learning is a novel part of Data Science and it encompasses the ability of machines to learn from examples.
-These models are categorized as either \textbf{\textit{Supervised}} or \textbf{\textit{Unsupervised}} Machine Learning models.
 
@@
 
-\subsection{Supervised Learning} %Dev Later
+The foundation of every current field of science is mathematics. Almost all data science methods have a strong mathematical underpinning, like machine learning.
+It comes as no surprise that to work as a top data scientist, you would completely need all the other beads of expertise-programming ability, some volume of business intelligence, and your unique analytical and curious mentality-about the data.
+But learning the machinery under the hood is still worth it, instead of just being the guy behind the wheel with no understanding of the car.
+A good awareness of the mathematical machinery behind the trendy algorithms would also give you an advantage over your colleagues.
+
+\section{Machine Learning}
+
+Machine Learning is a novel part of Data Science and it encompasses the ability of machines to learn from examples.
+These models are categorized as either \textbf{\textit{Supervised}} or \textbf{\textit{Unsupervised}} Machine Learning models.
+
+\subsection{Supervised Learning}
+Supervised learning is essentially a formalization of the notion of learning from formerly supervised fields of learning.
+The learner (usually, a computer programme) is presented with two data sets, a training set and a test set during supervised learning.
+The idea is to set the learner's training set test to learn 'from a set of classified examples in the training set such that unlabeled examples can be defined with the greatest expected precision in the test set.
+That is, the learner's goal is to create a law, a programme, or a process that classifies new examples by evaluating examples that already have a class \cite{learned2014introduction}
+
 Supervised learning is further categorized as  either \textbf{\textit{Regression}} or \textbf{\textit{Classification.}} The main difference between Regression and Classification is that the output variable in Regression is numerical while that for Classification is categorical.
@@
 
+A natural extension of multiple linear regression is multivariate linear regression in that both methods aim to explain hypothetical linear correlations between some variables of outputs and inputs.
+Multiple regression is focused on the analysis of the degree to which a set of "i" input variables X= (X1,Xi) influences the behaviour of a single output variable Y.
+The multivariate regression has "o" output variables Y= (Y1,Yo), each of which can be affected by precisely the same range of X= (X1,Xi) inputs.\cite{izenman2013multivariate}
+
 \subsubsection{Machine Learning model - Classification}
@@
 \subsection{Unsupervised Learning}
-%leave AS-_is
+Unsupervised learning is a category of ML methods that work in the dataset of unlabeled data in order to explore frameworks or trends.
+New paradigms for unsupervised learning (as such-called self-supervised learning) have also been introduced to manipulate multiple labels that are readily accessible to learn general purpose characteristics in addition to or within visual data.\cite{dayan1999unsupervised}
+Unsupervised learning explores how models should learn in a way that illustrates the mathematical form of the overall input sequence set to describe individual input sequence.
+In comparison to supervised learning or reinforcement learning, each feedback is not correlated with specific goal outcomes or environmental assessments; instead, the unsupervised learning incorporates previous prejudices as to what elements of the input system can be reflected in the output.\cite{dayan1999unsupervised}
 
@@
 Neural networks, in this context, apply to neuron frameworks, either biological or artificial in nature.
+
+\subsection{Biological Neural Network}
 Neural networks may respond to evolving inputs, so the network delivers the best possible outcome without the performance parameters having to be revamped.
@@
 
-\section{Recurring Neural Network}
+\subsection{Artificial Neural Network}
+
+To be developed.
+
+\section{Deep Neural Network}
 

### 2021-04-05 chapters/discussion.tex
methods and implementation

@@
 \section{Section title}
+
+In this work, an estimated relationship between wheat crop of Hungary and its GDP (indicated with GVP) is established.
+The work is inspired by extensive literature reviews and some previous related studies.
+In some of the studies artificial neural networks (ANN) were extensively used.
+It has been shown that recurrent networks, specifically its variants LSTM and GRU can perform much better.
+This can be verified comparing the results of FFNNs and RNNs in Figure ~\ref{fig:feedforward} and Figure ~\ref{fig:trg}.
+
+Although the results from GRU are promising, but it poses the challenge of training the network appropriately.
+Specifically, how the speed and accuracy can be balanced and made optimum.
+With all of its pros and cons, it has been able to cater to the problems dynamically and actively.
+Also, these networks can be employed to solve huge sets of problems.
+
+From the results in Figure ~\ref{fig:trg}, it can be concluded that wheat quantity and wheat yield can significantly affect the GDP.
+This is particularly true since a large number of other agriproducts are directly dependent on wheat production.
+If the wheat yield is good enough, it can not only meet the requirements of food, but it can help flourish several related food industries.
+These two factors can significantly contribute to the country GDP.
+Also, they can help boom the exports sector of the economy.
 \subsection{Subsection title}

### 2021-04-05 chapters/implementation.tex
methods and implementation

@@
 The process of collecting raw data from sources, transforming it so that it matches our system's requirements and loading it into a data-set is know as \textbf{ETL.} This \textit{acronym} represents \textit{Extract - Transform - Load.}
+
+In this section, description regarding data pre-processing, model training, and model validations will be presented.
+Before the core analysis begins, it will be appropriate to talk about the dataset itself.
 
@@
 
-This raw data set contains lots of columns which are not necessary. The next step will be to clean the data by dropping these unnecessary columns.
-
-\subsection{Data Extraction.}
-
-As mentioned in the previous chapter, the source of data for the purpose of this thesis was the Food and Agriculture Organization of the United Nations.
+As mentioned in the previous section, the source of data for the purpose of this thesis was the Food and Agriculture Organization of the United Nations.
 To achieve my goals I focused on the \textbf{Value Of Agricultural Production} and in particular the \textbf{Gross Production Value.} This value was gotten by multiplying agricultural gross production by the output prices.
 In the data-sets used in this thesis paper, the gross production value is expressed in US dollars.
+This raw data set contains lots of columns which are not necessary.
+it's necessary to clean the data by dropping the unnecessary columns.
+
+\subsection{Data Extraction}
+
+This work is focused on estimation of Gross-Production Value (GPV), indicative of GDP, based on wheat crop information of Hungary.
+Finding the right data was been quite tedious.
+The data set was collected  from the United Nations Food and Agriculture Organization (UN-FAO) databases.
+The goal was to estimate GPV as the function of agri-land (Hectares) used for wheat, wheat quantity (Tons) produced and the crop yield (Hg/Ha – Hectogram/Hectares).
+All four variables could not be found in a single data-set.
+They were found in four different data-sets, but from the single source.
+The pertinent data-sets contained too much extra and irrelevant information.
+Using Pandas, the data-sets were cleaned, and desired variables were collected into one data-set a tabular frame using the year as the index.
+A glimpse of the data-frame is shown below:
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.4\textwidth,height=\textheight,keepaspectratio]{fig/finaltable.png}
+	\caption{Concatenated Final Dataset}
+	\label{fig:CFD}
+\end{figure}
+
+The correlation strength between the variables of the system is shown in the Figure below.
+Light and yellow colors indicate a strong correlation, while deeper colors show weak relationship.
+The weakest correlation can be observed between agricultural area and the yield, although it looks illogical.
+This is because of the unique definition of yield performance.
+So, it can be said that they are independent from one another.
+Similarly, weaker correlation can be observed amongst area, wheat quantity and GPV.
+It can be concluded that they will affect each other less, but they cannot be termed as independent parameters.
+
+Finally, the most valuable observation from Figure~\ref{fig:Corr} is that GPV is a strong function of quantity, yield and area (in ascending order from the quantity variable to area).
+So, inclusion/exclusion of these variables will severely affect the accuracy.
+Although there are inter-dependencies, but such dependencies can be better taken care of by the proposed solution.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.35\textwidth]{fig/correlation.png}
+	\caption{Feature Correlation Heatmap}
+	\label{fig:Corr}
+\end{figure}
+
+\subsection{Data Cleaning}
 
@@
 
-\subsection{Data Cleaning} 
 The repetitive columns constitute noise which isn't required.
@@
 \section{Recurring Neural Network}
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.35\textwidth]{fig/rnn.png}
+	\caption{Recurrent Neural Network (RNN)}
+	\label{fig:rnn}
+\end{figure}
+A representative RNN is shown in Figure ~\ref{fig:rnn} showing the hidden layer.
+The updating of the weight is accomplished as the function of current inputs and previous outputs.
+Usually, the weights are updated on the basis of output gradients.
+The weights are only updated, if the underlying gradients are non-zero.
+As the learning goes on, gradients begin to vanish.
+At sometimes the gradients are zero, but they should not be.
+In deep learning literature, this phenomenon is termed as gradient-vanishing problem - GVP \cite{haykin2009neural}.
+To avoid GVP, two variants of RNNs have been proposed.
+LSTM (Long-Short Term Memory) recurrent neural network and GRU (Gated-Recurrent Unit).
+
+\subsubsection{LSTM-RNN}
+
+The problem of GVP can be solved in two ways, firstly using long-term and short-term memories and secondly using the first way in gated fashion.
+The first method is termed as long-term short-term memory.
+The short-term serves usually as RNN works, while long-term memory serves to keep the most relevant and updated information.
+Although, this method is computationally costly, it effectively overcomes the issue of vanishing gradients.
+
+A LSTM has a comparable control stream as a repetitive neural organization.
+It measures information passing on data as it engenders forward.
+The distinctions are the activities inside the LSTM's cells.
+These tasks are utilized to permit the LSTM to keep or fail to remember data.
+
+The central idea of LSTM is the cell state and its different doors.
+The cell state goes about as a vehicle thruway that moves relative data right down the grouping chain.
+You can consider it the "memory" of the organization.
+The cell state, in principle, can convey important data all through the handling of the grouping.
+So even data from the prior time steps can advance toward later time steps, decreasing the impacts of momentary memory.
+As the cell state goes on its excursion, data gets added or eliminated to the cell state by means of entryways.
+The entryways are diverse neural organizations that choose which data is permitted on the cell state.
+The doors can realize what data is pertinent to keep or fail to remember during preparing.
+
+\subsubsection{GRU}
+
+The Gated Recurrent Unit (GRU) can be seen as an improvement of the LSTM, which does not utilize unequivocal cell states.
+Another distinction is that the LSTM straightforwardly controls the measure of data changed in the hidden state utilizing separate response and forgetting gateways.
+Then again, a GRU utilizes a solitary reset entryway to accomplish a similar objective.
+Be that as it may, the fundamental thought in the GRU is similar to that of a LSTM, regarding how it somewhat resets the hidden states.
+
+The GRU is the fresher age of Recurrent Neural organizations and is quite like a LSTM.
+GRU utilizes the hidden state to move data.
+It likewise just has two entryways, a reset door and update door.
+The update door acts like the fail to remember and enter the entryway of a LSTM.
+It chooses what data to discard and what new data to add.
+
+The reset door is another entryway.
+It is utilized to choose how much past data not to remember.
+Furthermore, GRU has less tensor activities; accordingly, they are somewhat speedier to prepare than LSTMs.
+There is definitely not an unmistakable fact as to which one is better.
+Scientists and designers typically attempt both to figure out which one turns out better for their utilization case.
+
+To summarize, RNNs are useful for handling arrangement information for forecasts however they experience momentary memory.
+LSTM and GRU were made as a strategy to alleviate momentary memory utilizing components called gateways.
+Gates are simply neural organizations that control the progression of data coursing through the arrangement chain.
+LSTM and GRU are utilized in best-in-class profound learning applications like discourse acknowledgment, discourse amalgamation, common language understanding, and so on.
+
+\subsubsection{Topology}
+
+In this work, LSTM and GRU variants of recurrent networks have been used as computational machines.
+The results of these algorithms are compared with a feed-forward network.
+For all the networks the number of input neurons are three, with 64 hidden neurons and a single output neuron.
+
+In the feedforward network, 64 neurons are divided equally in 8 consecutive hidden layers.
+Although the network has become extremely complex, but the complexity remains essentially in vain.
+The training accuracy and prediction value were found to be poor.
+
+The structure of LSTM requires that some neurons be assigned to the memory making region, known as cell, which serves the purpose of holding long-term desired information.
+The training machines can assign different number of neurons to cell memory and to the hidden layer depending upon the user's choice.
+The decision, taken by the user are dictated by various factors.
+Larger amount of memory can improve accuracy of prediction hugely, but speed of consecutive predictive operations could be impeded.
+So, the decision should be taken based on the optimum between speed and accuracy.
+
+GRU does not require dedicated long-term memory, but it inherits the features of LSTM.
+It does update the neurons and lets them forget older data in similar fashion to that of LSTM.
+This algorithm can provide better speed and accuracy management.
+
+A representative Feed Forward Network is shown in Figure ~\ref{fig:feedforward} showing the resulting graph.
+
+We can conclude that this method will not serve our purpose.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.35\textwidth]{fig/epoch_accuracy.png}
+	\caption{Feed Forward Network}
+	\label{fig:feedforward}
+\end{figure}
+
+\subsubsection{Model Training}
+
+The models have been trained with extensive number of epochs.
+The training performance and achieved accuracy are shown in Figure ~\ref{fig:feedforward} and Figure ~\ref{fig:trg} respectively.
+The x-axis indicates the epoch number, while the y-axis indicates the training loss.
+From Figure ~\ref{fig:feedforward}, it should be noticed that even with 100 epochs, the performance of feed-forward network could not be improved.
+So, further analysis of this network is left out.
+Figure ~\ref{fig:train} indicates the training performance of the proposed RNN’s networks.
+As the training continues epoch-by-epoch, networks keep on learning the underlying system better and better.
+So, LSTM indicates some fluctuations, but they can be ignored in comparison to feedforward network.
+It can clearly be seen that accuracy of LSTM and GRU has surpassed that of feed-forward network.
+This might have occurred due to foundations of LSTM and GRU on recurrent networks.
+
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\includegraphics[width=0.35\textwidth]{fig/trg.png}
+		\caption{LSTM vs GRU I}
+		\label{fig:trg}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+			\centering
+		\includegraphics[width=0.35\textwidth]{fig/train.png}
+		\caption{LSTM vs GRU II}
+		\label{fig:train}
+	\end{subfigure}	
+	\caption{Training Performance between LSTM and GRU}
+\end{figure}
+
 \section{Deep Learning}
-
-\chapter{Results}
-\section{Neural Networks}
-In this section, I will describe the Progression from Normal Neural network to Recurring Neural Networks - RNN. In the end, I'll show that the GRU works well and I have solved what I set out to do. 
-it should be here
-\subsection{Subsection title}
-Neural Networks and more advanced technologies.
-Right now we use Pandas for everything and it's enough, except when it's not.
-The more advanced we go into tech, the more basic the Machine Learning tools.
-
-Some Machine Learning models are very dependent on used materials.
-SCI-KIT uses the most basic of Neural networks.
-What you'll notice from GPV-Take 1 is that you can't create modern systems with SCI-KIT because it is the highest level of abstraction.
-
-Here, I'll need to show the results of the Google Colab Notebook - Gross Production Value 1 and the abysmal results I got using SCI-KIT
-
-We use SCI-KIT for scaling. It implements it very well. Train - Test - Split
-\cite{ponce1989engineering}

### 2021-04-05 chapters/methods.tex
methods and implementation

@@
 These models are categorized as either \textbf{\textit{Supervised}} or \textbf{\textit{Unsupervised}} Machine Learning models.
+
+Although machine learning methods are more concerned with obtaining input/output variables, relational acceptability is still validated with statistical indicators.
+In GDP studies, several machine/deep learning techniques have been used.
+The effects of renewable energy production \cite{perera2014machine}, agri-growth conditioned by political stability is analyzed in  employing a huge set of statistical and ML methods.
+A replication study on the relationship between GDP and oil prices is reported in\cite{charfeddine2020reviewing}
+
+Commodity prices are also the reasonable predictors of GDP.
+COVID-19 has severely affected even large perpetually stable economies, a deep learning algorithm examined this impact \cite{jena2021impact}.
+An ANN method is reported in \cite{milavcic2017application}to establish validity of the most used effectors of GDP: services, manufacturing, industrial growth and agri-growth.
+Deep learning methods are also reported to predict recessions \cite{vrontos2020modeling} and the factors which can affect economic growth negatively.
 
@@
 Neural networks, in this context, apply to neuron frameworks, either biological or artificial in nature.
+Machine learning notions have become universally accepted tools in social, pure or applied sciences.
+Since this work uses neural networks, a note on neural networks will be presented.
 
@@
 Neural networks may respond to evolving inputs, so the network delivers the best possible outcome without the performance parameters having to be revamped.
-In the development of trading systems, the notion of neural networks, which has its origins in artificial intelligence, is rapidly gaining prominence.\citealp*{krose1993introduction}.
+In the development of trading systems, the notion of neural networks, which has its origins in artificial intelligence, is rapidly gaining prominence\cite{krose1993introduction}.
 
@@
 Finally, the amplitude of the output is regulated by an activation function.
-A reasonable performance range, for example, is usually between 0 and 1, or it may be −1 and 1.
+A reasonable performance range, for example, is usually between 0 and 1.
 
@@
 
-To be developed.
+Artificial Neural Networks are applied in regression studies where continuous responses are the most appropriate \cite{haykin2009neural}.
+They could be of type: feed-forward neural networks (FNN), recurrent neural networks (RNN), convolutional neural networks (CNN), radial-basis functions networks (RBFN) and modular neural networks (MNN) \cite{nielsen2015neural,goyal2013artificial,grossberg2013recurrent,ripley2007pattern}
+
+Some specific examples of research work in agriculture, where neural networks have been employed are presented here.
+These examples are in addition to the ones mentioned in previous section.
+In \cite{ghielmi2006descriptive} NNs have been used for crop yield estimation.
+While in \cite{goyal2013artificial} ANNs have been employed to understand the effects of food security.
 

### 2021-04-05 chapters/results.tex
methods and implementation

\section{Neural Networks}

In this section, I will describe the Progression from Normal Neural network to Recurring Neural Networks - RNN. In the end, I'll show that the GRU works well and I have solved what I set out to do. 
it should be here

In this section, various results of this research activity will be presented. The results will majorly be training and validation performance. From the above discussion, it should be noticed that GRU is performing extremely better than both feed-forward network and LSTM network. So, in the following discussion, performance of GRU will be described only.

\subsection{Training Results}

Training results pertain to how quickly and efficiently a given networks understands and learns its environment. The training efficiency of GRU is depicted in Figure ~\ref{fig:trg}, epoch number vs learning loss. The learning loss drastically decreases right from first epoch. Rapid decline continues until 40th epoch, then slowly reaches to zero before 100th epoch. This clearly indicates the superiority of GRU over LSTM and FFNN (feed-forward neural network). This performance clearly hints the best prediction accuracy of GRU.

\subsection{Validation}

Validation results are also shown in Figure ~\ref{fig:trg}, with x-axis showing the epoch number and y-axis showing the prediction error. 150 epochs have been employed to validate the model. Although validation does not approach to zeros exactly, but such a small error could be acceptable for the estimation of GPV. So, it does validate that GRU can perform the best amongst the class of recurrent neural networks. It looks like the efficient use of long-short memory has outclassed the performance of other networks.

\subsection{Subsection title}
Neural Networks and more advanced technologies. Right now we use Pandas for everything and it's enough, except when it's not. The more advanced we go into tech, the more basic the Machine Learning tools.

Some Machine Learning models are very dependent on used materials. SCI-KIT uses the most basic of Neural networks. What you'll notice from GPV-Take 1 is that you can't create modern systems with SCI-KIT because it is the highest level of abstraction.

Here, I'll need to show the results of the Google Colab Notebook - Gross Production Value 1 and the abysmal results I got using SCI-KIT

We use SCI-KIT for scaling. It implements it very well. Train - Test - Split
\cite{ponce1989engineering}

\subsection{Subsection title}

### 2021-04-10 chapters/methods.tex
Methods Reviewed

@@
 
-\textit{where} \textbf{H} is the current state, \textbf{ht-1} is the previous state and \textbf{Xt} is the inpunt state.
+\textit{where} \textbf{H} is the current state, \textbf{ht-1} is the previous state and \textbf{Xt} is the input state.
 
-\subsection{GRU}  % DOn't Touch
 \subsection{LSTM}
@@
 
-Testing my commit
+\subsection{Machine Learning vs Deep Learning}
 
-\section{Deep Learning}
-\subsection{Machine Learning vs Deep Learning}
+Machine and Deep learning both offer ways to train models and classify data.
+That is, learning from and classifying previous occurrences.
+In a standard Machine learning approach, we'll manually select the features in order to train the machine learning model.
+Those features are then referenced when analyzing and classifying new data.
+This is the standard workflow to solving a Machine learning problem.
+
+\begin{figure}[h!]
+	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/mlwkflow.png}
+	\caption{Machine Learning Workflow}
+	\label{fig:ML}
+\end{figure}
+
+Deep learning, which is a sub type of Machine learning, on the other hand skips the manual step of extracting features from the data set.
+Instead, the data is fed directly into the deep learning algorithm which then predicts the required outcome.
+
+\begin{figure}[H]
+	\includegraphics[width=\textwidth]{fig/dpwkflow.png}
+	\caption{Deep Learning Workflow}	
+	\label{fig:DL}
+\end{figure}
+
+In deciding whether to choose Machine or Deep learning, the question to be answered is whether there are lots of labeled data and a high-performance GPU.
+If these 2 factors are missing, then the right approach would be Machine learning.
+The reason for this is that Deep learning is generally more complex and highly accurate.
+One of the downsides to Deep learning is this: because the model is a black box, if something isn't working correctly, it might be hard to debug.

### 2021-04-12 chapters/implementation.tex
Extract_of_ETL

@@
 
+To extract data, apart from the source, which has already been mentioned as the FAO, the format has to be considered.
+Data can be provided in various formats like a csv file, xml file, json object just to mention a few.
+the extracted Data for my work was in a csv file format.
+
 This work is focused on estimation of Gross-Production Value (GPV), indicative of GDP, based on wheat crop information of Hungary.
-Finding the right data was been quite tedious.
-The data set was collected  from the United Nations Food and Agriculture Organization (UN-FAO) databases.
-The goal was to estimate GPV as the function of agri-land (Hectares) used for wheat, wheat quantity (Tons) produced and the crop yield (Hg/Ha – Hectogram/Hectares).
+The goal was to estimate GPV as the function of agri-land (Hectares) used for wheat, wheat quantity (Tons) produced and the crop yield (Hg/Ha Hectogram/Hectares).
 All four variables could not be found in a single data-set.
 They were found in four different data-sets, but from the single source.
-The pertinent data-sets contained too much extra and irrelevant information.
-Using Pandas, the data-sets were cleaned, and desired variables were collected into one data-set a tabular frame using the year as the index.
-A glimpse of the data-frame is shown below:
 
 \begin{figure}[h!]
-	\centering
-	\includegraphics[width=0.4\textwidth,height=\textheight,keepaspectratio]{fig/finaltable.png}
-	\caption{Concatenated Final Dataset}
-	\label{fig:CFD}
+	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/Area_Head.png}
+	\caption{Raw Data Area.}
+	\label{fig:Areaa_Head1}
 \end{figure}
+
+Figure \ref{fig:Areaa_Head1} shows the top 5 rows of the Wheat Area-harvested Data Set.
+
+\begin{figure}[h!]
+	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/Quantity_Head.png}
+	\caption{Raw Data Quantity.}
+	\label{fig:Quantity_Head}
+\end{figure}
+
+Figure \ref{fig:Quantity_Head} shows the top 5 rows of the Quantity Data Set.
+
+\begin{figure}[h!]
+	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/GPV_Head.png}
+	\caption{Raw Data Gross Production Value.}
+	\label{fig:GPV_Head}
+\end{figure}
+
+Figure \ref{fig:GPV_Head} shows the top 5 rows of the Gross Production Value Data Set.
 
@@
 
-\subsection{Data Cleaning}
+\subsection{Data Transformation}
+
+This is the data-validation step. The guiding principle is:
+
+\textquote{The garbage in, garbage out (GIGO) is the concept that flawed, or nonsense input data produces nonsense output or garbage}
+
+The pertinent data-sets contained too much extra and irrelevant information.
+Using Pandas, the data-sets were cleaned, and desired variables were collected into one data-set a tabular frame using the year as the index.
+A glimpse of the data-frame is shown below:
 
@@
 The approach to this was: \textit{Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.}
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.4\textwidth,height=\textheight,keepaspectratio]{fig/finaltable.png}
+	\caption{Concatenated Final Dataset}
+	\label{fig:CFD}
+\end{figure}
 
@@
 \end{lstlisting}
-
-\begin{figure}[h!]
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{fig/Area_Head.png}
-	\caption{Raw Data Area.}
-	\label{fig:Areaa_Head1}
-\end{figure}
-
-Figure \ref{fig:Areaa_Head1} shows the top 5 rows of the Data Set.
 
@@
 
-\section{Implementing Machine Learning Work Flow}
-
-\subsection{Assembling the Data Set}
-\section{How I implemented the Neural Networks}
+\section{Data Loading}
+\section{The Neural Networks}
 \section{Recurring Neural Network}

### 2021-04-12 chapters/implementation.tex
Implementation completed

@@
 \subsection{Data Extraction}
+
+Different data sets are available separately.
+For the purpose of this thesis, I narrowed down on wheat.
+I adopted a consistent time-frame (\textbf{1965 to 2002}).
+The approach to this was: \textit{Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.}
 
@@
 
-\textquote{The garbage in, garbage out (GIGO) is the concept that flawed, or nonsense input data produces nonsense output or garbage}
+\textquote{The garbage in, garbage out (GIGO) is the concept that flawed, or nonsense input data produces nonsense output or garbage.}
 
-The pertinent data-sets contained too much extra and irrelevant information.
-Using Pandas, the data-sets were cleaned, and desired variables were collected into one data-set a tabular frame using the year as the index.
+The pertinent data-sets contained too much extra and irrelevant information as well some null columns.
+Using Pandas, the data-sets were cleaned, irrelevant columns were dropped and desired variables were collected into one data-set a tabular frame using the year as the index.
 A glimpse of the data-frame is shown below:
-
-Different data sets are available separately.
-For the purpose of this thesis, I narrowed down on wheat.
-I adopted a consistent time-frame (\textbf{1965 to 2002}).
-The approach to this was: \textit{Given a set of features that are consistent with a particular agricultural product, the aim is to predict the Gross Production Value.}
 
@@
 The repetitive columns constitute noise which isn't required.
-I drop these to narrow down on the vital data necessary for my task.
+I dropped these to narrow down on the vital data necessary for my task.
 Two columns are left: \textit{"Year", "Value".} Since the word \textit{"Value"} appears in the different data-sets, it's renamed here as \textit{"Area(Hectares)"} to clearly indicate that this value refers to the measurement of the area.
@@
 
-A similar transformation is performed on the other data-sets. The resulting individual data-sets are: 
+A similar transformation is performed on the other data-sets. The resulting individual data-sets are displayed in Fig \ref{fig:heads} : 
 \begin{figure}
@@
 \section{Data Loading}
-\section{The Neural Networks}
+
+This is about loading the data to the database.
+Databases can be divided into either Relational or non-relational databases.
+Relational database store data in tables and rows.
+Non relation store data in JSON object.
+For the purpose of my work, the Python Pandas data-frame was used.
+This is a two-dimensional data structure where the data is aligned in rows and columns.
+The data can then be manipulated and vital information extracted.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.35\textwidth]{fig/panda.png}
+	\caption{Pandas DataFrame}
+	\label{fig:panda}
+\end{figure}
+
 \section{Recurring Neural Network}
@@
 \end{figure}
-
-\section{Deep Learning}

### 2021-04-15 chapters/implementation.tex
Results completed

@@
 \section{Data Science - Engineering}
-\todo{Demonstrate the ability for analysis.}
-\todo{Link to Related works - Not repeating. Might look at the sections and link them}
 
-\todo{Section 1 is very interesting and further supports, or cast doubts or raises question marks about what is being said in the Related works.}
 The process of collecting raw data from sources, transforming it so that it matches our system's requirements and loading it into a data-set is know as \textbf{ETL.} This \textit{acronym} represents \textit{Extract - Transform - Load.}
@@
 LSTM and GRU are utilized in best-in-class profound learning applications like discourse acknowledgment, discourse amalgamation, common language understanding, and so on.
-
-\subsubsection{Topology}
-
-In this work, LSTM and GRU variants of recurrent networks have been used as computational machines.
-The results of these algorithms are compared with a feed-forward network.
-For all the networks the number of input neurons are three, with 64 hidden neurons and a single output neuron.
-
-In the feedforward network, 64 neurons are divided equally in 8 consecutive hidden layers.
-Although the network has become extremely complex, but the complexity remains essentially in vain.
-The training accuracy and prediction value were found to be poor.
-
-The structure of LSTM requires that some neurons be assigned to the memory making region, known as cell, which serves the purpose of holding long-term desired information.
-The training machines can assign different number of neurons to cell memory and to the hidden layer depending upon the user's choice.
-The decision, taken by the user are dictated by various factors.
-Larger amount of memory can improve accuracy of prediction hugely, but speed of consecutive predictive operations could be impeded.
-So, the decision should be taken based on the optimum between speed and accuracy.
-
-GRU does not require dedicated long-term memory, but it inherits the features of LSTM.
-It does update the neurons and lets them forget older data in similar fashion to that of LSTM.
-This algorithm can provide better speed and accuracy management.
-
-A representative Feed Forward Network is shown in Figure ~\ref{fig:feedforward} showing the resulting graph.
-
-We can conclude that this method will not serve our purpose.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=0.35\textwidth]{fig/epoch_accuracy.png}
-	\caption{Feed Forward Network}
-	\label{fig:feedforward}
-\end{figure}
-
-\subsubsection{Model Training}
-
-The models have been trained with extensive number of epochs.
-The training performance and achieved accuracy are shown in Figure ~\ref{fig:feedforward} and Figure ~\ref{fig:trg} respectively.
-The x-axis indicates the epoch number, while the y-axis indicates the training loss.
-From Figure ~\ref{fig:feedforward}, it should be noticed that even with 100 epochs, the performance of feed-forward network could not be improved.
-So, further analysis of this network is left out.
-Figure ~\ref{fig:train} indicates the training performance of the proposed RNN’s networks.
-As the training continues epoch-by-epoch, networks keep on learning the underlying system better and better.
-So, LSTM indicates some fluctuations, but they can be ignored in comparison to feedforward network.
-It can clearly be seen that accuracy of LSTM and GRU has surpassed that of feed-forward network.
-This might have occurred due to foundations of LSTM and GRU on recurrent networks.
-
-\begin{figure}[h!]
-	\centering
-	\begin{subfigure}{.5\textwidth}
-		\includegraphics[width=0.35\textwidth]{fig/trg.png}
-		\caption{LSTM vs GRU I}
-		\label{fig:trg}
-	\end{subfigure}%
-	\begin{subfigure}{.5\textwidth}
-			\centering
-		\includegraphics[width=0.35\textwidth]{fig/train.png}
-		\caption{LSTM vs GRU II}
-		\label{fig:train}
-	\end{subfigure}	
-	\caption{Training Performance between LSTM and GRU}
-\end{figure}

### 2021-04-15 chapters/results.tex
Results completed

@@
 In this section, I will describe the Progression from Normal Neural network to Recurring Neural Networks - RNN. In the end, I'll show that the GRU works well and I have solved what I set out to do.
-it should be here
 
-In this section, various results of this research activity will be presented.
+The various results of this research activity will be presented.
 The results will majorly be training and validation performance.
 From the above discussion, it should be noticed that GRU is performing extremely better than both feed-forward network and LSTM network.
-So, in the following discussion, performance of GRU will be described only.
 
@@
 The learning loss drastically decreases right from first epoch.
-Rapid decline continues until 40th epoch, then slowly reaches to zero before 100th epoch.
+Rapid decline continues until the 40th epoch, then slowly reaches to zero before the 100th epoch.
 This clearly indicates the superiority of GRU over LSTM and FFNN (feed-forward neural network).
@@
 
-\subsection{Subsection title}
+\subsubsection{Topology}
+
+In this work, LSTM and GRU variants of recurrent networks have been used as computational machines.
+The results of these algorithms are compared with a feed-forward network.
+For all the networks the number of input neurons are three, with 64 hidden neurons and a single output neuron.
+
+In the feedforward network, 64 neurons are divided equally in 8 consecutive hidden layers.
+Although the network has become extremely complex, but the complexity remains essentially in vain.
+The training accuracy and prediction value were found to be poor.
+
+The structure of LSTM requires that some neurons be assigned to the memory making region, known as cell, which serves the purpose of holding long-term desired information.
+The training machines can assign different number of neurons to cell memory and to the hidden layer depending upon the user's choice.
+The decision, taken by the user are dictated by various factors.
+Larger amount of memory can improve accuracy of prediction hugely, but speed of consecutive predictive operations could be impeded.
+So, the decision should be taken based on the optimum between speed and accuracy.
+
+GRU does not require dedicated long-term memory, but it inherits the features of LSTM.
+It does update the neurons and lets them forget older data in similar fashion to that of LSTM.
+This algorithm can provide better speed and accuracy management.
+
+A representative Feed Forward Network is shown in Figure ~\ref{fig:feedforward} showing the resulting graph.
+
+We can conclude that this method will not serve our purpose.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.35\textwidth]{fig/epoch_accuracy.png}
+	\caption{Feed Forward Network}
+	\label{fig:feedforward}
+\end{figure}
+
+\subsubsection{Model Training}
+
+The models have been trained with extensive number of epochs.
+The training performance and achieved accuracy are shown in Figure ~\ref{fig:feedforward} and Figure ~\ref{fig:trg} respectively.
+The x-axis indicates the epoch number, while the y-axis indicates the training loss.
+From Figure ~\ref{fig:feedforward}, it should be noticed that even with 100 epochs, the performance of feed-forward network could not be improved.
+So, further analysis of this network is left out.
+Figure ~\ref{fig:train} indicates the training performance of the proposed RNN’s networks.
+As the training continues epoch-by-epoch, networks keep on learning the underlying system better and better.
+So, LSTM indicates some fluctuations, but they can be ignored in comparison to feedforward network.
+It can clearly be seen that accuracy of LSTM and GRU has surpassed that of feed-forward network.
+This might have occurred due to foundations of LSTM and GRU on recurrent networks.
+
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}{.5\textwidth}
+		\includegraphics[width=0.35\textwidth]{fig/trg.png}
+		\caption{LSTM vs GRU I}
+		\label{fig:trg}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=0.35\textwidth]{fig/train.png}
+		\caption{LSTM vs GRU II}
+		\label{fig:train}
+	\end{subfigure}	
+	\caption{Training Performance between LSTM and GRU}
+\end{figure}
+
+\section{Model GUI}
+
+Abubakar Abid's \cite{abid2019gradio} research highlights the challenge of accessing machine learning models.
+According to him, the accessibility challenge makes collaboration more difficult.
+To improve accessibility, he and his team developed Gradio.
+
+Gradio is a Python library that generates an easy-to-use UI for machine learning models.
+Access to the model is as easy as sharing a URL.
+This solution was not without its drawbacks.
+Because this app in still a work-in-progress, the URL is only valid for 6 hours.
+In order to provide a workaround this problem, i deployed the Gradio UI to Heroku.

### 2021-04-15 paper.tex
Intro-Abstract(100%)-Related Works(50%)
Related Works completed
methods and implementation
Methods Reviewed
Results completed

@@
 \usepackage[colorinlistoftodos]{todonotes}
+\usepackage{csquotes}
+\usepackage{dblfloatfix}
+
+\definecolor{pblue}{rgb}{0.13,0.13,1}
+\definecolor{pgreen}{rgb}{0,0.5,0}
+\definecolor{pred}{rgb}{0.9,0,0}
+\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
 
@@
 }
+\usepackage{float}
 \usepackage{graphicx}
 \graphicspath{{fig/}}
+%
+\makeatletter
+\setlength{\@fptop}{0pt}
+\makeatother
+%
 
@@
 
-\todo{This is has to be concise. What is the purpose of my Thesis? What is the aim and the Objectives
-for researching this particular area}
-
 Gross Domestic Product (GDP) is one of the most popular economical term and parameter for the indication of the well-being of a country.
@@
 
-This research is focused on the use of deep learning methods to study the impact of agriculture on the economy of Hungary. It focuses on:
+The objective of this research is to use predictive deep learning methods to study the impact of an agriculture crop, in this case wheat, on the economy of Hungary. It focuses on:
 
@@
 \chapter{Related Works}
-\todo{Also known as Literature. Concise. Here, I have to create a diagram that shows my thought process.}
 
@@
 
+\chapter{Results}
+\input{chapters/results}
+
 \chapter{Discussion}
@@
 \bibliography{reference}
+
 \end{document}
